### 2016-10-19 draft.tex
Initial Commit.
what happened

[ticket: X]

\documentclass{ifacconf}

\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{amsmath, amssymb}
\usepackage{natbib}            % you should have natbib.sty
\usepackage{graphicx}          % Include this line if your 
                               % document contains figures,
%\usepackage[dvips]{epsfig}    % or this line, depending on which
                               % you prefer.
% predefined environments
%\begin{thm} ... \end{thm}		% Theorem
%\begin{lem} ... \end{lem}		% Lemma
%\begin{claim} ... \end{claim}	% Claim
%\begin{conj} ... \end{conj}	% Conjecture
%\begin{cor} ... \end{cor}		% Corollary
%\begin{fact} ... \end{fact}	% Fact
%\begin{hypo} ... \end{hypo}	% Hypothesis
%\begin{prop} ... \end{prop}	% Proposition
%\begin{crit} ... \end{crit}	% Criterion
%\begin{rem} ... \end{rem}    % Remark
%\begin{pf} ... \end{pf}      % Proof
%\begin{ack} ... end{ack}     % Acknowledgement

\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\norm}[1]{\left\|#1\right\|}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\green}[1]{\textcolor[rgb]{0,.5,0}{#1}}
\newcommand{\red}{\textcolor{red}}

\allowdisplaybreaks[3]

\begin{document}

\begin{frontmatter}

\title{Approximating the Maximal Positive Invariant Set of Parameter Uncertain Linear System}%\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

\author{Rainer M. Schaich} 
\author{Mark Cannon}
\author{Sina Ober-Bl\"obaum}

\address{Department of Engineering Science, University of Oxford, OX1 3PJ, UK. (e-mail: \{rainer.schaich,mark.cannon,sina.ober-blobaum\}@eng.ox.ac.uk).}

\begin{keyword}                           % Five to ten keywords,  
Keyword 1; keyword 2;
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

\begin{abstract}                          % Abstract of not more than 250 words.
Abstract goes here.
\end{abstract}

\end{frontmatter}

\section{Introduction}
%
%
\section{Set Operations for Parametrically Convex Sets}
%
%
\section{Multiplicative to Additive Approximation}

\section{Computational Examples}

\section{Conclusion}
\end{document}

### 2016-10-19 ifacconf.tex
Initial Commit.
what happened

[ticket: X]

%===============================================================================
% $Id: ifacconf.tex 19 2011-10-27 09:32:13Z jpuente $  
% Template for IFAC meeting papers
% Copyright (c) 2007-2008 International Federation of Automatic Control
%===============================================================================
\documentclass{ifacconf}

\usepackage{graphicx}      % include this line if your document contains figures
\usepackage{natbib}        % required for bibliography
%===============================================================================
\begin{document}
\begin{frontmatter}

\title{Style for IFAC Conferences \& Symposia: Use Title Case for
  Paper Title\thanksref{footnoteinfo}} 
% Title, preferably not more than 10 words.

\thanks[footnoteinfo]{Sponsor and financial support acknowledgment
goes here. Paper titles should be written in uppercase and lowercase
letters, not all uppercase.}

\author[Oxford]{First A. Author}

\address[Oxford]{}

\begin{abstract}                % Abstract of not more than 250 words.
These instructions give you guidelines for preparing papers for IFAC
technical meetings. Please use this document as a template to prepare
your manuscript. For submission guidelines, follow instructions on
paper submission system as well as the event website.
\end{abstract}

\begin{keyword}
Five to ten keywords, preferably chosen from the IFAC keyword list.
\end{keyword}

\end{frontmatter}
%===============================================================================

\section{Introduction}
This document is a template for \LaTeXe. If you are reading a paper or
PDF version of this document, please download the electronic file
\texttt{ifacconf.tex}. You will also need the class file
\texttt{ifacconf.cls}. Both files are available on the IFAC web site.

Please stick to the format defined by the \texttt{ifacconf} class, and
do not change the margins or the general layout of the paper. It
is especially important that you do not put any running header/footer
or page number in the submitted paper.\footnote{
This is the default for the provided class file.}
Use \emph{italics} for emphasis; do not underline.

Page limits may vary from conference to conference. Please observe the 
page limits of the event for which your paper is intended.

\section{Procedure for Paper Submission}

Next we see a few subsections.

\subsection{Review Stage}

For submission guidelines, follow instructions on paper submission
system as well as the event website.

Note that conferences impose strict page limits, so it will be better
for you to prepare your initial submission in the camera ready layout
so that you will have a good estimate for the paper
length. Additionally, the effort required for final submission will be
minimal.

\subsection{Equations}

Some words might be appropriate describing equation~(\ref{eq:sample}), if 
we had but time and space enough.

\begin{equation} \label{eq:sample}
{{\partial F}\over {\partial t}} = D{{\partial^2 F}\over {\partial x^2}}.
\end{equation}

See \cite{Abl:56}, \cite{AbTaRu:54}, \cite{Keo:58} and \cite{Pow:85}.

\subsubsection{Example.} This equation goes far beyond the
celebrated theorem ascribed to the great Pythagoras by his followers.

\begin{thm}   % use the thm environment for theorems
The square of the length of the hypotenuse of a right triangle equals
the sum of the squares of the lengths of the other two sides.
\end{thm}

\begin{pf}    % and the pf environment for proofs
The square of the length of the hypotenuse of a right triangle equals the sum of the squares 
of the lengths of the other two sides.
\end{pf}

%% There are a number of predefined theorem-like environments in
%% ifacconf.cls:
%%
%% \begin{thm} ... \end{thm}            % Theorem
%% \begin{lem} ... \end{lem}            % Lemma
%% \begin{claim} ... \end{claim}        % Claim
%% \begin{conj} ... \end{conj}          % Conjecture
%% \begin{cor} ... \end{cor}            % Corollary
%% \begin{fact} ... \end{fact}          % Fact
%% \begin{hypo} ... \end{hypo}          % Hypothesis
%% \begin{prop} ... \end{prop}          % Proposition
%% \begin{crit} ... \end{crit}          % Criterion

Of course LaTeX manages equations through built-in macros. You may
wish to use the \texttt{amstex} package for enhanced math
capabilities.

\subsection{Figures}

To insert figures, use the \texttt{graphicx} package. Although other
graphics packages can also be used, \texttt{graphicx} is simpler to
use. See  Fig.~\ref{fig:bifurcation} for an example.

\begin{figure}
\begin{center}
\includegraphics[width=8.4cm]{bifurcation}    % The printed column width is 8.4 cm.
\caption{Bifurcation: Plot of local maxima of $x$ with damping $a$ decreasing} 
\label{fig:bifurcation}
\end{center}
\end{figure}

Figures must be centered, and have a caption at the bottom.

\subsection{Tables}
Tables must be centered and have a caption above them, numbered with
Arabic numerals. See table~\ref{tb:margins} for an example.

\begin{table}[hb]
\begin{center}
\caption{Margin settings}\label{tb:margins}
\begin{tabular}{cccc}
Page & Top & Bottom & Left/Right \\\hline
First & 3.5 & 2.5 & 1.5 \\
Rest & 2.5 & 2.5 & 1.5 \\ \hline
\end{tabular}
\end{center}
\end{table}

\subsection{Final Stage}

Authors are expected to mind the margins diligently.  Papers need to
be stamped with event data and paginated for inclusion in the
proceedings. If your manuscript bleeds into margins, you will be
required to resubmit and delay the proceedings preparation in the
process.

\subsubsection{Page margins.} See table~\ref{tb:margins} for the
page margins specification. All dimensions are in \emph{centimeters}.

\subsection{PDF Creation}

All fonts must be embedded/subsetted in the PDF file. Use one of the
following tools to produce a good quality PDF file:

\subsubsection{PDFLaTeX} is a special version of LaTeX by Han The
Thanh which produces PDF output directly using Type-1 fonts instead of
the standard \texttt{dvi} file. It accepts figures in JPEG, PNG, and PDF
formats, but not PostScript. Encapsulated PostScript figures can be
converted to PDF with the \texttt{epstopdf} tool or with Adobe Acrobat
Distiller.

\subsubsection{Generating PDF from PostScript} is the classical way of
producing PDF files from LaTeX. The steps are:

\begin{enumerate}
  \item Produce a \texttt{dvi} file by running \texttt{latex} twice.
  \item Produce a PostScript (\texttt{ps}) file with \texttt{dvips}.
  \item Produce a PDF file with \texttt{ps2pdf} or Adobe Acrobat
  Distiller.
\end{enumerate}

\subsection{Copyright Form}

IFAC will put in place an electronic copyright transfer system in due
course. Please \emph{do not} send copyright forms by mail or fax. More
information on this will be made available on IFAC website.

\section{Units}

Use SI as primary units. Other units may be used as secondary units
(in parentheses). This applies to papers in data storage. For example,
write ``$15\,\mathrm{Gb}/\mathrm{cm}^2$ ($100\,\mathrm{Gb}/\mathrm{in}^2$)''. 
An exception is when
English units are used as identifiers in trade, such as ``3.5 in
disk drive''. Avoid combining SI and other units, such as current in
amperes and magnetic field in oersteds. This often leads to confusion
because equations do not balance dimensionally. If you must use mixed
units, clearly state the units for each quantity in an equation.  The
SI unit for magnetic field strength $\mathbf{H}$ is $\mathrm{A}/\mathrm{m}$. However, if you wish to
use units of $\mathrm{T}$, either refer to magnetic flux density $\mathbf{B}$ or
magnetic field strength symbolized as $\mu_0\,\mathbf{H}$. Use the center dot to
separate compound units, e.g., ``$\mathrm{A} \cdot \mathrm{m}^2$''.

\section{Helpful Hints}

\subsection{Figures and Tables}

Figure axis labels are often a source of confusion. Use words rather
than symbols. As an example, write the quantity ``Magnetization'', or
``Magnetization M'', not just ``M''. Put units in parentheses. Do not
label axes only with units.  For example, write ``Magnetization
($\mathrm{A}/\mathrm{m}$)'' or ``Magnetization ($\mathrm{A} \mathrm{m}^{-1}$)'', not just
 ``$\mathrm{A}/\mathrm{m}$''. Do not
label axes with a ratio of quantities and units. For example, write
``Temperature ($\mathrm{K}$)'', not ``$\mbox{Temperature}/\mathrm{K}$''.

Multipliers can be especially confusing. Write ``Magnetization
($\mathrm{kA}/\mathrm{m}$)'' or ``Magnetization ($10^3 \mathrm{A}/\mathrm{m}$)''. Do not write
``Magnetization $(\mathrm{A}/\mathrm{m}) \times 1000$'' because the reader would not know
whether the axis label means $16000\,\mathrm{A}/\mathrm{m}$ or $0.016\,\mathrm{A}/\mathrm{m}$.

\subsection{References}

Use Harvard style references (see at the end of this document). With
\LaTeX, you can process an external bibliography database 
using \texttt{bibtex},\footnote{In this case you will also need the \texttt{ifacconf.bst}
file, which is part of the \texttt{ifaconf} package.}
or insert it directly into the reference section. Footnotes should be avoided as
far as possible.  Please note that the references at the end of this
document are in the preferred referencing style. Papers that have not
been published should be cited as ``unpublished''.  Capitalize only the
first word in a paper title, except for proper nouns and element
symbols.

\subsection{Abbreviations and Acronyms}

Define abbreviations and acronyms the first time they are used in the
text, even after they have already been defined in the
abstract. Abbreviations such as IFAC, SI, ac, and dc do not have to be
defined. Abbreviations that incorporate periods should not have
spaces: write ``C.N.R.S.'', not ``C. N. R. S.'' Do not use abbreviations
in the title unless they are unavoidable (for example, ``IFAC'' in the
title of this article).

\subsection{Equations}

Number equations consecutively with equation numbers in parentheses
flush with the right margin, as in (\ref{eq:sample}).  To make your equations more
compact, you may use the solidus ($/$), the $\exp$ function, or
appropriate exponents. Use parentheses to avoid ambiguities in
denominators. Punctuate equations when they are part of a sentence, as
in

\begin{equation} \label{eq:sample2}
\begin{array}{ll}
\int_0^{r_2} & F (r, \varphi ) dr d\varphi = [\sigma r_2 / (2 \mu_0 )] \\
& \cdot \int_0^{\inf} exp(-\lambda |z_j - z_i |) \lambda^{-1} J_1 (\lambda  r_2 ) J_0 (\lambda r_i ) d\lambda 
\end{array}
\end{equation}

Be sure that the symbols in your equation have been defined before the
equation appears or immediately following. Italicize symbols ($T$
might refer to temperature, but T is the unit tesla). Refer to
``(\ref{eq:sample})'', not ``Eq. (\ref{eq:sample})'' or ``equation
(\ref{eq:sample})'', except at the beginning of a sentence: ``Equation
(\ref{eq:sample}) is \ldots''.

\subsection{Other Recommendations}

Use one space after periods and colons. Hyphenate complex modifiers:
``zero-field-cooled magnetization''. Avoid dangling participles, such
as, ``Using (1), the potential was calculated'' (it is not clear who or
what used (1)). Write instead: ``The potential was calculated by using
(1)'', or ``Using (1), we calculated the potential''.

A parenthetical statement at the end of a sentence is punctuated
outside of the closing parenthesis (like this). (A parenthetical
sentence is punctuated within the parentheses.) Avoid contractions;
for example, write ``do not'' instead of ``don' t''. The serial comma
is preferred: ``A, B, and C'' instead of ``A, B and C''.

\section{Conclusion}

A conclusion section is not required. Although a conclusion may review
the main points of the paper, do not replicate the abstract as the
conclusion. A conclusion might elaborate on the importance of the work
or suggest applications and extensions.

\begin{ack}
Place acknowledgments here.
\end{ack}

\bibliography{ifacconf}             % bib file to produce the bibliography
                                                     % with bibtex (preferred)

%\begin{thebibliography}{xx}  % you can also add the bibliography by hand

%\bibitem[Able(1956)]{Abl:56}
%B.C. Able.
%\newblock Nucleic acid content of microscope.
%\newblock \emph{Nature}, 135:\penalty0 7--9, 1956.

%\bibitem[Able et~al.(1954)Able, Tagg, and Rush]{AbTaRu:54}
%B.C. Able, R.A. Tagg, and M.~Rush.
%\newblock Enzyme-catalyzed cellular transanimations.
%\newblock In A.F. Round, editor, \emph{Advances in Enzymology}, volume~2, pages
%  125--247. Academic Press, New York, 3rd edition, 1954.

%\bibitem[Keohane(1958)]{Keo:58}
%R.~Keohane.
%\newblock \emph{Power and Interdependence: World Politics in Transitions}.
%\newblock Little, Brown \& Co., Boston, 1958.

%\bibitem[Powers(1985)]{Pow:85}
%T.~Powers.
%\newblock Is there a way out?
%\newblock \emph{Harpers}, pages 35--47, June 1985.

%\bibitem[Soukhanov(1992)]{Heritage:92}
%A.~H. Soukhanov, editor.
%\newblock \emph{{The American Heritage. Dictionary of the American Language}}.
%\newblock Houghton Mifflin Company, 1992.

%\end{thebibliography}

\appendix
\section{A summary of Latin grammar}    % Each appendix must have a short title.
\section{Some Latin vocabulary}              % Sections and subsections are supported  
                                                                         % in the appendices.
\end{document}

### 2016-10-24 draft.tex
Essentially first draft.
what happened

[ticket: X]

@@
 \usepackage{enumerate}
-\usepackage{amsmath, amssymb}
+\usepackage{amsmath, amssymb,mathrsfs}
 \usepackage{natbib}            % you should have natbib.sty
@@
                                % you prefer.
+
+\usepackage{tikz,environ}
+\usetikzlibrary{arrows,positioning,patterns,decorations.pathreplacing}
+
+\tikzset{
+    at xy split/.style 2 args={
+        at={(#1,#2)}
+    },
+    a/.style={circle, draw=red},`'
+    b/.style={rectangle, draw=blue}
+}
+
+\makeatletter
+\newsavebox{\measure@tikzpicture}
+\NewEnviron{scaletikzpicturetowidth}[1]{%
+  \def\tikz@width{#1}%
+  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
+  \BODY
+  \end{lrbox}%
+  \pgfmathparse{#1/\wd\measure@tikzpicture}%
+  \edef\tikzscale{\pgfmathresult}%
+  \BODY
+}
+\makeatother
+
 % predefined environments
@@
 
+\providecommand{\conv}{\text{conv}}
+\providecommand{\vol}{\text{vol}}
+\providecommand{\spann}{\text{span}}
+\providecommand{\C}{\mathcal C}
+\providecommand{\E}{\mathcal E}
+\providecommand{\W}{\mathcal W}
+\providecommand{\V}{\mathcal V}
+\providecommand{\X}{\mathcal X}
+\providecommand{\Y}{\mathcal Y}
+\providecommand{\U}{\mathcal U}
+\providecommand{\R}{\mathcal R}
+\providecommand{\T}{\mathcal T}
+\providecommand{\D}{\mathscr D}
+\providecommand{\PP}{\mathbb P}
+\providecommand{\RR}{\mathbb R}
+\providecommand{\bfa}[1]{\mathbf{#1}}
+
+\newcommand*{\Resize}[1]{\resizebox{\columnwidth}{!}{$#1$}}
+
 \allowdisplaybreaks[3]
@@
 
-\title{Approximating the Maximal Positive Invariant Set of Parameter Uncertain Linear System}%\thanksref{footnoteinfo}} 
+\title{Maximising the Guaranteed Feasible Set for Uncertain MPC Schemes with Probabilistic Constraints}%\thanksref{footnoteinfo}} 
 % Title, preferably not more than 10 words.
@@
 \author{Mark Cannon}
-\author{Sina Ober-Bl\"obaum}
 
-\address{Department of Engineering Science, University of Oxford, OX1 3PJ, UK. (e-mail: \{rainer.schaich,mark.cannon,sina.ober-blobaum\}@eng.ox.ac.uk).}
+\address{Department of Engineering Science, University of Oxford, OX1 3PJ, UK. (e-mail: \{rainer.schaich,mark.cannon\}@eng.ox.ac.uk).}
 
@@
 %
-\section{Set Operations for Parametrically Convex Sets}
+Determining positive invariant sets for uncertain linear systems has been discussed in the literature for decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
+%
+Properties of such sets and the algorithms to compute them have are known and documented in the literature.
+%
+In addition to pure analysis purposes, these sets are often used as terminal constraint sets in model predictive control formulations in order to guarantee the feasibility of the control scheme at all times, see e.g.~\cite{Mayne2014}.
+%
+To be able to apply the methods presented in~\cite{Kolmanovsky:1998} and~\cite{blanchini:2007} the modelled uncertainty has to be constrained to known convex set, in particular a polytope or a ellipsoid.
+%
+If constraints on the system do not have to be satisfied for all possible uncertainties but merely for a subset satisfying some probabilistic condition, sampling based methods can be applied, see e.g.~\cite{Margellos2014,Zhang2015}.
+%
+However, the sets determined based on sampled uncertainties are computationally expensive to obtain and guaranties can only be given in a stochastic sense, i.e. with a certain confidence level.
+%
+The method presented in~\cite{Zhang2015} is based on determining a certain set in which the probabilistic requirements are met and using that set for subsequent analysis.
+%
+This concept does not require sampling for simple probability distributions, instead we can explicitly parametrise an auxiliary set in which all probabilistic conditions are met.
+%
+Using such a parametrised set, we can optimise the size of the positive invariant set for the particular set in order to produce the largest positive invariant set while guaranteeing satisfaction of the probabilistic constraints, hence approximating the positive invariant set of the original problem.
+%
+Unlike sample based approaches this method inherently guarantees probabilistic constraint satisfaction.
+
+In order to use a stochastically constrained system in a robust model predictive control setup while introducing a minimal amount of conservatism a closed-loop min-max formulation has to be applied~\cite{Lee:1997}, this requires the determination of additional constraints.
+%
+The n-step controllable set for a given target set (see e.g.~\cite{bertsekas71}) is determined in such a way that there exists an admissible input sequence for every state in the n-step controllable set such that after n~steps the system state is in the target set for any admissible uncertainty.
+%
+Using the same parametrisation the stochastic constraint can be replaced by a computationally convenient set operation guaranteeing the satisfaction of the original specification.
+%
+By maximising the size of the n-step controllable set we indirectly approximate the n-step controllable set of the probabilistically constrained system.
+
+The remainder of this paper elaborates the method in the following way:
+%
+In section~\ref{sec:setup} we present the considered problem formulation and derive conditions for the guaranteed positive invariant set in subsection~\ref{ssec:approximating:MRPI} and for the guaranteed n-step controllable set in subsection~\ref{ssec:approximating:n:step}.
+%
+The parametrisation of a parallelotope is discussed in~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
+%
+Two numerical examples are presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the presentation and sketch possible extensions to the presented scheme.
+
+The following notation is used in the sequel: $A\oplus B = \{x:x=a+b,a\in A,b\in B\}$ denotes the Minkowski addition, $A\ominus B = \{x: x+b \in A\forall b\in B\}$ the Pontryagin difference, for a real set $C\subset\RR^d$ we denote the image of $C$ under the linear map $A:\RR^d\rightarrow\RR^d$ by $AC = \{y\in\RR^d:Ax=y,x\in C\}$ and the pre-image $A^{-1}C = \{y\in\RR^d:Ay\in C\}$.
+%
+We denote the probability of an event $E$ by $\PP\{E\}$, throughout this paper we assume the probability density to be uniform.
+
+\section{Setup}\label{sec:setup}
+%
+
+The discrete time system we consider is given by
+%
+\begin{equation}
+	x^+ = Ax + Bu + w
+\end{equation}
+%
+with the state constraints $x\in\X = \{x\in\RR^d:E_ix\leq 1, i\leq M_\X\}$, the input~$u\in\U = \{u\in\RR^{q_\U}:F_i u\leq 1, i\leq M_\U\}$ and an uncertain variable $w\in\W = \{w\in\RR^{q_\W}:G_i w\leq 1,i\leq M_\W\}$.
+%
+We furthermore consider the auxiliary output variable 
+%
+\begin{equation}
+	y = Cx + Du + v
+\end{equation}
+%
+which is subject to a random variable $v\in\V = \{v\in\RR^{q_\Y}:\Gamma_i v\leq 1,i\in M_\V\}$ for which the probability distribution is assumed to be uniform.
+%
+The output is probabilistically constrained to satisfy
+%
+\begin{equation}\label{eq:probabilistic:constraint}
+	\PP\{y\in\Y\}\geq p.
+\end{equation}
+%
+with $\Y=\{y\in\RR^{q_\Y}:H_i y\leq h_i, i\leq M_\Y\}$.
+
+Notice that for any $\V^\prime\subseteq\V$ with $\frac{\vol(\V^\prime)}{\vol(\V)}\geq p$ we have $\PP\{Cx+Du + v\in\Y\forall v\in\V^\prime\}\geq p$, where $Cx+Du+v\in\Y$ for all $v\in\V^\prime$ can easily be enforced by constraining $x$ and $u$.
+%
+Furthermore, by choosing $\V^\prime$ to be polytopic the equivalent constraints on $x$ and $u$ are polytopic and can easily be determined.
+%
+In the sequel of this paper we discuss how~$\V^\prime$ can be chosen in order to obtain the largest guaranteed n-step controllable set for a given target set, guaranteed positive invariant set.
+
+\subsection{Approximating the guaranteed invariant set}\label{ssec:approximating:MRPI}
+%
+First we discuss how we can extend existing methods to calculate the maximal robust positive invariant (MRPI) set (see e.g.~\cite{blanchini:2007}) in such a way that all states produce only feasible successor states for a given feedback controller $u = Kx$.
+%
+I.e. an invariant set for which all possible trajectories satisfy state constraints and probabilistic constraint at all time.
+%
+\begin{equation}\label{eq:alternative:MRPI:set}
+	X^\infty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+	&x_k\in\X\\
+	&(C+DK)x_k+v\in\Y\\
+	&\forall w_j\in\W,v\in \V^\prime,k\geq 0\end{aligned} \right\}
+\end{equation}
+%
+It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\X^\infty$:
+%
+\begin{equation}
+	\X^\infty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+	&x_k\in\X\\
+	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
+	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}
+\end{equation}
+%
+The inclusion $X^\infty\subseteq\X^\infty$ holds for any $\V^\prime\subseteq\V$ with the appropriate probability measure, therefore maximising the volume of $X^\infty$ improves the approximation of $\X^\infty$.
+
+In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions met in~\eqref{eq:alternative:MRPI:set} we introduce the set of all possible successor states~$\D_k(X)$ of states in $X$ at time $k$:
+%
+\begin{equation}\begin{split}
+	\D_k(X) &= (A+BK)^{k}X\oplus\W\oplus\dots\oplus(A+BK)^{k-1}\W\\
+	&= (A+BK)^k X\oplus \bigoplus_{i=0}^{k-1}(A+BK)^i\W
+\end{split}\end{equation}
+%
+Using $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate condition~\eqref{eq:alternative:MRPI:set} to
+%
+\begin{equation}\label{eq:containment:condition:alternative:MRPI}
+\D_k(X^\infty)\subseteq\X\cap\R
+\end{equation}
+%
+for all $k\geq0$.
+%
+With this identity we can determine a direct way of determining $X^\infty$:
+%
+\begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
+	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
+\end{equation}
+%
+Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore using available methods it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined.
+%
+In order to computationally determine $X^\infty$ we define the recursive sequence
+%
+\begin{equation}\label{eq:MRPI:sequence}
+	\begin{split}
+	X_0 &= \X\\
+	Z_k &= X_k\cap\R\\
+	X_{k+1} &= Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
+	\end{split}
+\end{equation}
+%
+Notice that $X_k = \bigcap_{l\leq k}\E_l$ and therefore the recursion terminates, analogue to the conventional MRPI calculation, once $X_k\subseteq X_{k+1}$.
+
+\begin{thm}
+Iteration~\eqref{eq:MRPI:sequence} terminates after a finite number of iterations~$N$, such that $X_{N+1}=X_N$ and $X_N=X^\infty$.
+\end{thm}
+%
+\begin{pf}
+Do we need one?!
+\end{pf}
+
+The optimisation program to approximate the positive invariant set $\X^\infty$ can therefore be formulated as
+%
+\begin{subequations}\label{seq:optimisation:MRPI:abstract}
+	\begin{equation}
+		\max_{\V^\prime} \vol(X^\infty)
+	\end{equation}
+%
+	subject to
+%
+\begin{equation}
+	\V^\prime\subseteq\V
+\end{equation}
+%
+\begin{equation}
+	\vol(\V^\prime)\geq p\cdot\vol(\V)
+\end{equation}
+\end{subequations}
+%
+In section~\ref{sec:volume:of:hypercube} we will discuss how an optimisation can be solved using parallelotopes for~$\V^\prime$.
+
+\subsection{Approximating the n-step controllable set}\label{ssec:approximating:n:step}
+%
+We now turn our attention to the n-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
+%
+That is the set of all states such that a sequence of admissible inputs exists that takes any state $x\in\C_n$ to the target set $x_n\in\T$ for any admissible disturbance sequence $w\in\W$ while guaranteeing state- and probabilistic constraint satisfaction.
+%
+This set is given by
+%
+\begin{equation}
+	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+	&x_N\in\T\\
+	&x_k\in\X\\
+	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
+	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
+\end{equation}
+%
+Again, it is trivial to see that the set
+%
+\begin{equation}
+	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+	&x_N\in\T\\
+	&x_k\in\X\\
+	&(C+DK)x_k+v\in\Y\\
+	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
+\end{equation}
+%
+is always contained in $\C_n$ for any admissible choice of $\V^\prime\subseteq\V$.
+%
+As in the case of the positive invariant set, fixing $\V^\prime$ to be polytopic leads to a computationally tractable algorithm yielding~$C_n$ to be a polytopic approximation of~$\C_n$, and optimising over~$\V^\prime$ to maximise the volume of~$C_n$ indirectly improves the approximation of $\C_n$.
+%
+It is known that $C_n(\T) = C^n_1(\T) = C_1(C_1(\dots C_1(\T)\dots))$ (see e.g.~\cite{blanchini:2007}), which allows the use of simple computational geometry algorithms.
+
+In particular the one-step controllable set $C_1(\T)$ for $\T = \{x\in\RR^d:J_i x\leq1,i\leq M_\T\}$ is given by the projection of 
+%
+\begin{equation}
+	L_1(\T) = \left\{(x,u):\begin{aligned}
+	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
+	Ax+Bu+w\in\T\;\forall w\in\W
+	\end{aligned}\right\}
+\end{equation}
+%
+onto $\RR^d$.
+%
+As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.
+
+The optimisation approximating the n-step controllable set $\C_n(\T)$ is then given as
+%
+\begin{subequations}\label{seq:optimisation:n:step:set:abstract}
+	\begin{equation}
+		\max_{\V^\prime} \vol(C_n(\T))
+	\end{equation}
+	subject to
+	\begin{equation}
+	\V^\prime\subseteq\V
+\end{equation}
+%
+\begin{equation}
+	\vol(\V^\prime)\geq p\cdot\vol(\V)
+\end{equation}
+\end{subequations}
+
+\section{The Volume of a Transformed Hypercube}\label{sec:volume:of:hypercube}
 %
 %
-\section{Multiplicative to Additive Approximation}
+In this section we present a method allowing us to optimise over polytopes as required to solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract}.
+%
+For this we consider the class of parallelotopes (see e.g.~\cite{Coxeter:1973}), i.e. the minimal zonotope in $\RR^d$, $\spann(v_1,\dots,v_d) = \{x:\exists 0\leq t_i\leq1, x = \sum_{i=1}^d t_iv_i\}$.
+%
+It is well known that the volume of a parallelotope is given by
+%
+\begin{equation}
+	\vol(\spann(v_1,\dots,v_d)) = \abs{\det(v_1,\dots,v_d)}.
+\end{equation}
+%
+Recall that $\det(\lambda v_1,\dots,v_d) = \lambda\det(v_1,\dots,v_d)$, therefore we have that for fixed $v_1,\dots,v_d$ the volume of $\spann(t_1v_1,\dots,t_dv_d)$ with $0<t_i\leq1$ is given by
+%
+\begin{equation}
+	\vol(\spann(t_1v_1,\dots,t_dv_d)) = \abs{\det(v_1,\dots,v_d)}\prod_{i=1}^d t_i
+\end{equation}
+%
+It is known that the volume of an object is translation invariant, i.e.
+$\vol(\spann(t_1v_1,\dots,t_dv_d)\oplus\{v_0\}) = \vol(\spann(t_1v_1+v_0,\dots,t_dv_d+v_0)) = \vol(\spann(t_1v_1,\dots,t_dv_d))$.
 
-\section{Computational Examples}
+By using $v_0$ and $t_i$ as decision variables we can solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract} by solving an optimisation program with $2d$ decision variables.
+%
+All geometric calculations necessary to compute~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract} can be performed using the vertex description of $\V^\prime$, which can easily be shown to be
+%
+\begin{equation}
+	\V^\prime = \underset{i\leq 2^d}{\conv}\{(t_1v_1,\dots,t_dv_d)\lambda_i+v_0\}
+\end{equation}
+%
+where $\lambda_i$ are the vertices of the unit box $U = \{\lambda\in\RR^d:0\leq\lambda_i\leq 1\}$.
 
-\section{Conclusion}
+The problem formulation~\eqref{seq:optimisation:MRPI:abstract} can therefore be reformulated as
+%
+\begin{subequations}\label{seq:optimisation:MRPI:precise}
+\begin{equation}
+	\max_{v_0,t_1,\dots,t_d} \vol(X^\infty)
+\end{equation}
+subject to
+\begin{equation}\label{eq:containment:linear:1}
+	\Gamma((t_1v_1,\dots,t_dv_d)\lambda_i+v_0)\leq \bfa{1}, i\leq 2^d \Leftrightarrow \V^\prime\subseteq\V
+\end{equation}
+%
+\begin{equation}
+	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} \Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
+\end{equation}
+%
+\begin{equation}\label{eq:linear:inequalites:on:t:1}
+	0<t_i\leq1, i\leq d
+\end{equation}
+\end{subequations}
+%
+analogous for~\eqref{seq:optimisation:n:step:set:abstract}
+%
+\begin{subequations}\label{seq:optimisation:n:step:precise}
+\begin{equation}
+	\max_{v_0,t_1,\dots,t_d} \vol(C_n(\T))
+\end{equation}
+subject to
+\begin{equation}\label{eq:containment:linear:2}
+	\Gamma((t_1v_1,\dots,t_dv_d)\lambda_i+v_0)\leq \bfa{1}, i\leq 2^d \Leftrightarrow \V^\prime\subseteq\V
+\end{equation}
+%
+\begin{equation}
+	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} \Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
+\end{equation}
+%
+\begin{equation}\label{eq:linear:inequalites:on:t:2}
+	0<t_i\leq1, i\leq d
+\end{equation}
+\end{subequations}
+%
+Notice that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq const.$ is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+%
+The uniqueness of a maximiser for the volume of a set however is less transparent and can in general not be guaranteed.
+
+\section{Computational Examples}\label{sec:examples}
+%
+%
+%
+In this section we present a two dimensional example for each proposed scheme.
+%
+First we illustrate the approximation of the guaranteed positive invariant set~$X^\infty$ for the system
+%
+\begin{equation}\label{eq:example:system:MRPI}
+	x^+ = \begin{pmatrix}0.7&-0.25\\0.25&0.7\end{pmatrix}x+\begin{pmatrix}0\\1\end{pmatrix}u+w
+\end{equation}
+%
+subject to the constraints $\X = \{x:\norm{x}_\infty\leq15\}$, $\U = \{u:\abs{u}\leq2\}$ and $\W=\{w:\norm{w}_1\leq1\}$.
+%
+The output 
+%
+\begin{equation}
+	y = \begin{pmatrix}-0.08&-0.05\\
+   -0.14&   -0.04\end{pmatrix}x + \begin{pmatrix}
+0.44\\0.44\end{pmatrix}u + v
+\end{equation}
+%
+is subject to the probabilistic constraint
+%
+\begin{equation}
+	\PP\{\norm{y}_\infty\leq 1\}\geq 0.3
+\end{equation}
+%
+for 
+%
+$$
+\V = \conv\{\begin{pmatrix}\pm0.08\\0\end{pmatrix},\begin{pmatrix}0\\\pm0.07\end{pmatrix}\}.
+$$
+%
+To compute a feedback controller $u=Kx$ we use a LQR design with $Q=I$ and $R=1$.
+%
+As span vectors we use $v_1 = (0.07,0.08)^T$ and $v_2 = (-0.07,0.08)^T$, which means that $\V^\prime$ is a scaled version of $\V$.
+%
+Although we can not make statements on convexity of the volume in this parametrisation the optimisation converges to the same maximiser for different initialisers, furthermore numeric evaluation of the Hessian at the maximiser reveals that one eigenvalue vanishes.
+%
+The resulting set is illustrated in Figure~\ref{fig:MRPI:optimised}.
+%
+\begin{figure}
+\includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
+\caption{The guaranteed positive invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the original invariant set initialised using $t_1=t_2=\sqrt{0.3005}$ and $v_0 = (0,-0.01)^T$.}
+\label{fig:MRPI:optimised}
+\end{figure}
+
+For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$.
+%
+Again the result illustrated in figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+%
+
+\begin{figure}
+\includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
+\caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue).
+The additional sets are remaining $C_1(\T),C_2(\T)$ and $C_3(\T)$ for the initialiser and the optimised~$\V^\prime$.}
+\label{fig:n:step:controllable:set}
+\end{figure}
+
+\section{Conclusion}\label{sec:conclusion}
+%
+%
+In this paper we presented a method in which the positive invariant set and the n-step controllable set of a stochastically constrained system are approximated respectively.
+%
+The method we present is based on a simple restriction of the set $\V^\prime\subseteq$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
+%
+Although the presented scheme scales well to higher dimensions, the complexity of positive invariant sets and n-step controllable sets does not.
+%
+The underlying probability distribution was assumed to be uniform for ease of presentation, a similar method may be applied as long as the probability measure of a parallelotope can be analytically determined.
+%
+An additional improvement to the n-step controllable set $C_n(\T)$ could be obtained by introducing $\V_1^\prime,\dots,\V_{n-1}^\prime$, to allow different sets $\V_i^\prime$ at each stage introducing $(n-1)\times 2d$ additional decision variables.
+
+\bibliographystyle{alpha}
+\bibliography{MyBibliography}
 \end{document}

### 2016-10-26 draft.tex
Updated draft.
what happened

[ticket: X]

@@
 \providecommand{\spann}{\text{span}}
+\providecommand{\B}{\mathcal B}
 \providecommand{\C}{\mathcal C}
@@
 \providecommand{\Y}{\mathcal Y}
+\providecommand{\Z}{\mathcal Z}
 \providecommand{\U}{\mathcal U}
@@
 %
-If constraints on the system do not have to be satisfied for all possible uncertainties but merely for a subset satisfying some probabilistic condition, sampling based methods can be applied, see e.g.~\cite{Margellos2014,Zhang2015}.
+If constraints on the system do not have to be satisfied for all possible uncertainties but merely for a subset then the problem becomes a chance constrained problem, see e.g.~\cite{Kall2010}.
+%
+Control formulations of this kind can be addressed using a range of techniques including scenario optimization, see e.g.~\cite{Calafiore2010}, and sampling based methods, e.g.~\cite{Margellos2014,Zhang2015}.
 %
@@
 %
-The method presented in~\cite{Zhang2015} is based on determining a certain set in which the probabilistic requirements are met and using that set for subsequent analysis.
+The method presented in~\cite{Zhang2015} is based on determining a certain set in which the probabilistic requirements are met with a given confidence and using that set for subsequent analysis.
 %
@@
 Unlike sample based approaches this method inherently guarantees probabilistic constraint satisfaction.
+
+A similar principle of using sets of a set probability measure is used in p-efficiency theory, see~\cite{Dentcheva2009}, where the distribution is not required to be simple but the structure of the chance constraints is restrictive.
 
@@
 We denote the probability of an event $E$ by $\PP\{E\}$, throughout this paper we assume the probability density to be uniform.
+%
+The set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball centred at the origin, for a matrix $\Gamma\in\RR^{m\times n}$ the notation $\Gamma x\leq \bfa{1}$ is to be understood element-wise, where $\bfa{1}$ is a vector of ones in $\RR^m$.
 
@@
 \begin{equation}\label{eq:probabilistic:constraint}
-	\PP\{y\in\Y\}\geq p.
+	\PP\{ v \in \mathcal{V} : y = Cx + Du + v \in \mathcal{Y} \}\geq p.
 \end{equation}
@@
 
-Notice that for any $\V^\prime\subseteq\V$ with $\frac{\vol(\V^\prime)}{\vol(\V)}\geq p$ we have $\PP\{Cx+Du + v\in\Y\forall v\in\V^\prime\}\geq p$, where $Cx+Du+v\in\Y$ for all $v\in\V^\prime$ can easily be enforced by constraining $x$ and $u$.
+We not use the following proposition.
 %
-Furthermore, by choosing $\V^\prime$ to be polytopic the equivalent constraints on $x$ and $u$ are polytopic and can easily be determined.
+\begin{prop}
+Let $v\in\V$ be a uniformly distributed random variable, let $\V^\prime\subseteq\V$ such that $\vol(\V^\prime)\geq p$, then every $q\in\Z\ominus\V^\prime$ satisfies $\PP\{q+v\in\Z\}\geq p$.
+\end{prop}
 %
+\begin{pf}
+%
+Using that $\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} = \PP\{\V^\prime\} = \vol(\V^\prime)$ for all $q\in\Z\ominus\V^\prime$ we have
+%
+\begin{equation}\begin{split}
+&\PP\{q+v\in\Z\} = \PP\{\{q\}\oplus\V\subseteq\Z\} = \\
+&\PP\{\{q\}\oplus(\V^\prime\cup(\V\setminus\V^\prime))\subseteq\Z\} = \\
+&\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} + \PP\{\{q\}\oplus(\V\setminus\V^\prime)\subseteq\Z\}\geq \\
+&\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} =\vol(\V^\prime)\geq p.
+\end{split}\end{equation}
+%
+\end{pf}
+%
+Notice that for polytopic $\Z$ and $\V^\prime$ the set $\Z\ominus\V^\prime$ can be computed explicitly and is itself polytopic.
+
 In the sequel of this paper we discuss how~$\V^\prime$ can be chosen in order to obtain the largest guaranteed n-step controllable set for a given target set, guaranteed positive invariant set.
@@
 \begin{thm}
-Iteration~\eqref{eq:MRPI:sequence} terminates after a finite number of iterations~$N$, such that $X_{N+1}=X_N$ and $X_N=X^\infty$.
+Let $\Gamma$ be a map such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $((A+BK),\Gamma)$ be observable, then iteration~\eqref{eq:MRPI:sequence} terminates after a finite number of iterations~$N$, such that $X_{N+1}=X_N$ and $X_N=X^\infty$.
 \end{thm}
@@
 \begin{pf}
-Do we need one?!
+%
+The observability of $((A+BK),\Gamma)$ implies that $X_d$ is compact, since $X_{d-1}\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k}\X\subseteq\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1}\} = \{x:\pm\Gamma Ox\leq \bfa{1}\}$ for the observability matrix~$O$ which has full rank.
+
+Let~$P$ be such that $(A+BK)^TP(A+BK)\leq\rho^2P$ holds for $\rho$ denoting the spectral radius of $A+BK$.
+%
+To see that $\E_k$ grows exponentially let $\W\subseteq\B_P(r)$ then
+%
+\begin{equation}\begin{split}
+	&\bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
+	&\subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P(\sum_{i=0}^{k-1}\rho^i r)\subseteq\B_P(\frac{r}{1-\rho})
+\end{split}\end{equation}
+%
+i.e. $\E_k$ consists of an expanding minuend and a bounded subtrahend.
+%
+Therefore $\E_k$ expands exponentially, since $X_{d-1}$ is bounded there exists an integer~$N$ such that $X_{N}\cap\E_{N+1}=X_N$ hence $X_N=X^\infty$.
+%
 \end{pf}
@@
 \end{subequations}
+
+\begin{rem}
+The goal of reformulating a chance constrained model predictive control setup using the proposed method would be to minimise the introduced conservatism.
+%
+To achieve the best possible performance while guaranteeing constraint satisfaction a closed loop min-max model predictive control problem would be formulated, see e.g.~\cite{Lee:1997}.
+%
+This means that at each stage the decision variables are constrained to be such that the successor state is guaranteed to lie on a feasible trajectory to the target set.
+%
+So that if a chance constrained model predictive control problem is reformulated as a deterministically constrained problem guaranteeing probabilistic feasibility, the sets $C_n(\T)$ would play the role of stage constraints with the target set $\T=X^\infty$ to guarantee recursive feasibility.
+\end{rem}
 

### 2016-10-31 draft.tex
Updated Example.
what happened

[ticket: X]

@@
 %
-The resulting set is illustrated in Figure~\ref{fig:MRPI:optimised}.
+
+In order to compare the proposed method with existing results we compute a sample based set as described in~\cite{Zhang2015}, that is we compute the smallest set containing enough samples guarantee constraint satisfaction with a confidence of $1-\beta$.
+%
+To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation is given as
+%
+\begin{equation}\label{eq:comparison:set}\begin{split}
+	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
+	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
+\end{split}\end{equation}
+%
+Where $\bfa{v}^{(j)}$ are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=1e-3$, the number of samples necessary to satisfy this requirement is given by cumulative binomial distribution but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for our choice $N = 4714$.
+%
+The resulting sets are illustrated in Figure~\ref{fig:MRPI:optimised}.
 %
@@
 \includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
-\caption{The guaranteed positive invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the original invariant set initialised using $t_1=t_2=\sqrt{0.3005}$ and $v_0 = (0,-0.01)^T$.}
+\caption{The guaranteed positive invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the robust positive invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
 \label{fig:MRPI:optimised}
@@
 %
-
 \begin{figure}
@@
 \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue).
-The additional sets are remaining $C_1(\T),C_2(\T)$ and $C_3(\T)$ for the initialiser and the optimised~$\V^\prime$.}
+The additional sets are remaining $C_1(\T),C_2(\T)$ and $C_3(\T)$ for the comparison set obtained with~\eqref{eq:comparison:set} and the optimised~$\V^\prime$ obtained with the proposed method.}
 \label{fig:n:step:controllable:set}

### 2016-11-04 tmp.tex
edits 1
various edits (more to follow)

--- 2016-10-31 draft.tex
@@
 %
-Determining positive invariant sets for uncertain linear systems has been discussed in the literature for decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
+Positively invariant sets for uncertain linear systems have been researched for several decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
 %
-Properties of such sets and the algorithms to compute them have are known and documented in the literature.
+The properties of such sets and the algorithms to compute them are well known and documented in the literature.
 %
-In addition to pure analysis purposes, these sets are often used as terminal constraint sets in model predictive control formulations in order to guarantee the feasibility of the control scheme at all times, see e.g.~\cite{Mayne2014}.
+As well as being objects of interest in their own right,
+%In addition to pure analysis purposes, 
+these sets are often used as terminal constraint sets in model predictive control formulations, since in order to guarantee the feasibility of the control scheme at all times, see e.g.~\cite{Mayne2014}.
 %

### 2016-11-04 draft.tex
more edits

@@
 
+\def\bpf{\textnormal{\textit{Proof:}\hspace{1ex}}}
+\def\epf{\hfill \mbox{\qed}}%$\Box$}
+
 % predefined environments
@@
 \providecommand{\spann}{\text{span}}
+\newcommand{\Obs}{\mathcal{O}}
 \providecommand{\B}{\mathcal B}
@@
 
-\allowdisplaybreaks[3]
+%\allowdisplaybreaks[1]
 
@@
 
-\title{Maximising the Guaranteed Feasible Set for Uncertain MPC Schemes with Probabilistic Constraints}%\thanksref{footnoteinfo}} 
+\title{Maximising the guaranteed feasible set for uncertain MPC schemes with probabilistic constraints}%\thanksref{footnoteinfo}} 
 % Title, preferably not more than 10 words.
@@
 \author{Rainer M. Schaich} 
-\author{Mark Cannon}
+\qquad\qquad\author{Mark Cannon}
 
-\address{Department of Engineering Science, University of Oxford, OX1 3PJ, UK. (e-mail: \{rainer.schaich,mark.cannon\}@eng.ox.ac.uk).}
+\address{\mbox{Department of Engineering Science, University of Oxford, OX1 3PJ, UK} e-mail: \{rainer.schaich,mark.cannon\}@eng.ox.ac.uk}
 
@@
 \begin{abstract}                          % Abstract of not more than 250 words.
-Abstract goes here.
+This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to chance constraints.
+The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints; in contrast existing methods based on random sampling are only able to satisfy such constraints with a certain level of confidence.
+The proposed approach uses explicitly parametrised auxiliary disturbance sets, which are optimised so as to maximise the relevant positively invariant or $n$-step controllable set.
+The results are illustrated by numerical examples.
 \end{abstract}
@@
 %
-Determining positive invariant sets for uncertain linear systems has been discussed in the literature for decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
+Positively invariant sets for uncertain linear systems have been researched for several decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
 %
-Properties of such sets and the algorithms to compute them have are known and documented in the literature.
+The properties of such sets and the algorithms to compute them are well known and documented in the literature.
 %
-In addition to pure analysis purposes, these sets are often used as terminal constraint sets in model predictive control formulations in order to guarantee the feasibility of the control scheme at all times, see e.g.~\cite{Mayne2014}.
+As well as being objects of interest in their own right,
+%In addition to pure analysis purposes, 
+these sets are often used as terminal constraint sets model predictive control in order to guarantee the feasibility of the control scheme at all times \citep[see e.g.][]{Mayne2014}.
 %
-To be able to apply the methods presented in~\cite{Kolmanovsky:1998} and~\cite{blanchini:2007} the modelled uncertainty has to be constrained to known convex set, in particular a polytope or a ellipsoid.
+
+For the methods presented in~\cite{Kolmanovsky:1998} and~\cite{blanchini:2007} to be applicable, the modelled uncertainty has to be constrained to a known disturbance set, in particular a convex polytopic or ellipsoidal set.
 %
-If constraints on the system do not have to be satisfied for all possible uncertainties but merely for a subset then the problem becomes a chance constrained problem, see e.g.~\cite{Kall2010}.
+If constraints on the system do not have to be satisfied for all uncertainty realisations but instead are invoked for an arbitrary subset of the uncertainty set of sufficient size (or probability measure), then the problem becomes a chance constrained problem \cite[see e.g.][]{Kall1994}.
 %
-Control formulations of this kind can be addressed using a range of techniques including scenario optimization, see e.g.~\cite{Calafiore2010}, and sampling based methods, e.g.~\cite{Margellos2014,Zhang2015}.
+Control formulations of this kind can be addressed using a range of techniques including scenario optimization \citep[e.g.][]{Calafiore2010}, and sampling-based methods, \citep[e.g.][]{Margellos2014,Zhang2015,Fleming2016}.
 %
-However, the sets determined based on sampled uncertainties are computationally expensive to obtain and guaranties can only be given in a stochastic sense, i.e. with a certain confidence level.
+
+Positively invariant sets based on samples of uncertain model parameters are often computationally expensive to determine and guarantees can only be given in a stochastic sense, namely with a certain confidence level.
 %
-The method presented in~\cite{Zhang2015} is based on determining a certain set in which the probabilistic requirements are met with a given confidence and using that set for subsequent analysis.
+The method presented in~\cite{Zhang2015} determines a set in which the probabilistic requirements are met with a given confidence and uses that set for subsequent analysis.
 %
-This concept does not require sampling for simple probability distributions, instead we can explicitly parametrise an auxiliary set in which all probabilistic conditions are met.
+However, for simple probability distributions, this approach does not require sampling; instead we can explicitly parametrise an auxiliary disturbance set in which all probabilistic conditions are met.
 %
-Using such a parametrised set, we can optimise the size of the positive invariant set for the particular set in order to produce the largest positive invariant set while guaranteeing satisfaction of the probabilistic constraints, hence approximating the positive invariant set of the original problem.
+Using such a parametrised set, we can perform an optimisation
+%the size of the positively invariant set 
+%for the particular set 
+in order to compute the largest positively invariant set while guaranteeing satisfaction of the probabilistic constraints, hence approximating the maximal positively invariant set for a chance-constrained problem.
 %
-Unlike sample based approaches this method inherently guarantees probabilistic constraint satisfaction.
+Unlike sample based approaches, this method ensures probabilistic constraint satisfaction with certainty (rather than with a confidence level less than $1$, which is the case for sample-based methods).
+%
+A similar principle of using parametrised sets of a specified probability measure is used in $p$-efficiency theory~\citep{Dentcheva2009}, where the distribution is not required to be simple but the structure of the chance constraints is restrictive.
 
-A similar principle of using sets of a set probability measure is used in p-efficiency theory, see~\cite{Dentcheva2009}, where the distribution is not required to be simple but the structure of the chance constraints is restrictive.
+In order to formulate a robust model predictive control law for a chance constrained stochastic system while introducing a minimal amount of conservatism, we consider a closed-loop min-max formulation~\citep{Lee:1997}.
+This requires the determination of additional constraints.
+%
+The $n$-step controllable set for a given horizon $n$ and target set \citep[see e.g.][]{bertsekas71} has the property that, for every state in the $n$-step controllable set, there exists an admissible input sequence such that the system state enters the target set after $n$ steps, for any admissible sequence of uncertainty realisations.
+%
+Using a parametrised uncertainty set with specified probabilistic properties, chance constraints can be replaced by computationally convenient set operations that guarantee the satisfaction of the original chance constraints.
+%
+By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the probabilistically constrained system.
 
-In order to use a stochastically constrained system in a robust model predictive control setup while introducing a minimal amount of conservatism a closed-loop min-max formulation has to be applied~\cite{Lee:1997}, this requires the determination of additional constraints.
+%The remainder of this paper elaborates the method in the following way:
 %
-The n-step controllable set for a given target set (see e.g.~\cite{bertsekas71}) is determined in such a way that there exists an admissible input sequence for every state in the n-step controllable set such that after n~steps the system state is in the target set for any admissible uncertainty.
-%
-Using the same parametrisation the stochastic constraint can be replaced by a computationally convenient set operation guaranteeing the satisfaction of the original specification.
-%
-By maximising the size of the n-step controllable set we indirectly approximate the n-step controllable set of the probabilistically constrained system.
-
-The remainder of this paper elaborates the method in the following way:
-%
-In section~\ref{sec:setup} we present the considered problem formulation and derive conditions for the guaranteed positive invariant set in subsection~\ref{ssec:approximating:MRPI} and for the guaranteed n-step controllable set in subsection~\ref{ssec:approximating:n:step}.
+This paper is organised  as follows:
+In section~\ref{sec:setup} we present the considered problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, the conditions for the positively invariant set under chance constraints.
+The corresponding conditions for the $n$-step controllable set are derived in section~\ref{ssec:approximating:n:step}.
 %
@@
 
-The following notation is used in the sequel: $A\oplus B = \{x:x=a+b,a\in A,b\in B\}$ denotes the Minkowski addition, $A\ominus B = \{x: x+b \in A\forall b\in B\}$ the Pontryagin difference, for a real set $C\subset\RR^d$ we denote the image of $C$ under the linear map $A:\RR^d\rightarrow\RR^d$ by $AC = \{y\in\RR^d:Ax=y,x\in C\}$ and the pre-image $A^{-1}C = \{y\in\RR^d:Ay\in C\}$.
+The following notation is employed: $A\oplus B = \{x:x=a+b,\, a\in A,\, b\in B\}$ denotes the Minkowski addition, $A\ominus B = \{x: x+b \in A \, \forall b\in B\}$ the Pontryagin difference, for a real set $C\subset\RR^d$ we denote the image of $C$ under the linear map $A:\RR^d\rightarrow\RR^d$ by $AC = \{y\in\RR^d:Ax=y,x\in C\}$ and the pre-image $A^{-1}C = \{y\in\RR^d:Ay\in C\}$.
 %
@@
 %
-The set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball centred at the origin, for a matrix $\Gamma\in\RR^{m\times n}$ the notation $\Gamma x\leq \bfa{1}$ is to be understood element-wise, where $\bfa{1}$ is a vector of ones in $\RR^m$.
+The set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball of radius $r$ centred at the origin, for a matrix $\Gamma\in\RR^{m\times n}$ the notation $\Gamma x\leq \bfa{1}$ is to be understood element-wise, where $\bfa{1}$ is a vector of ones in $\RR^m$.
 
-\section{Setup}\label{sec:setup}
+\section{Problem formulation}\label{sec:setup}
 %
@@
 %
-with the state constraints $x\in\X = \{x\in\RR^d:E_ix\leq 1, i\leq M_\X\}$, the input~$u\in\U = \{u\in\RR^{q_\U}:F_i u\leq 1, i\leq M_\U\}$ and an uncertain variable $w\in\W = \{w\in\RR^{q_\W}:G_i w\leq 1,i\leq M_\W\}$.
+with state $x$ and control input $u$ subject to the constraints 
+\begin{align*}
+&x \in\X = \bigl\{x\in\RR^d : E_ix\leq 1, \ i\leq M_\X\bigr\}, \\
+&u\in\U = \bigl\{u\in\RR^{q_\U} : F_i u\leq 1, \ i\leq M_\U\bigr\},
+\end{align*} 
+and with disturbance input $w$ subject to the constraints
+\[
+w\in\W = \bigl\{w\in\RR^{q_\W}:G_i w\leq 1,\ i\leq M_\W \bigr\}.
+\]
 %
@@
 %
-which is subject to a random variable $v\in\V = \{v\in\RR^{q_\Y}:\Gamma_i v\leq 1,i\in M_\V\}$ for which the probability distribution is assumed to be uniform.
+which depends on a random variable $v$:
+\[
+v\in\V = \bigl\{v\in\RR^{q_\Y}:\Gamma_i v\leq 1, \ i\in M_\V\bigr\},
+\]
+for which the probability distribution is assumed to be uniform.
 %
@@
 \begin{equation}\label{eq:probabilistic:constraint}
-	\PP\{ v \in \mathcal{V} : y = Cx + Du + v \in \mathcal{Y} \}\geq p.
+	\PP\bigl\{ v \in \mathcal{V} : y = Cx + Du + v \in \mathcal{Y} \bigr\}\geq p.
 \end{equation}
 %
-with $\Y=\{y\in\RR^{q_\Y}:H_i y\leq h_i, i\leq M_\Y\}$.
+with
+\[
+\Y=\bigl\{y\in\RR^{q_\Y} : H_i y\leq h_i, \ i\leq M_\Y\bigr\}.
+\]
 
-We not use the following proposition.
+We make  use of the following proposition.
 %
-\begin{prop}
+
+\vspace{0.5\baselineskip}\begin{prop}
 Let $v\in\V$ be a uniformly distributed random variable, let $\V^\prime\subseteq\V$ such that $\vol(\V^\prime)\geq p$, then every $q\in\Z\ominus\V^\prime$ satisfies $\PP\{q+v\in\Z\}\geq p$.
@@
 %
-\begin{pf}
+\bpf
 %
-Using that $\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} = \PP\{\V^\prime\} = \vol(\V^\prime)$ for all $q\in\Z\ominus\V^\prime$ we have
+Using the fact that $\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} = \PP\{\V^\prime\} = \vol(\V^\prime)$ for all $q\in\Z\ominus\V^\prime$ we have
 %
 \begin{equation}\begin{split}
-&\PP\{q+v\in\Z\} = \PP\{\{q\}\oplus\V\subseteq\Z\} = \\
-&\PP\{\{q\}\oplus(\V^\prime\cup(\V\setminus\V^\prime))\subseteq\Z\} = \\
-&\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} + \PP\{\{q\}\oplus(\V\setminus\V^\prime)\subseteq\Z\}\geq \\
-&\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} =\vol(\V^\prime)\geq p.
+&\PP\{q+v\in\Z\} = \PP\{\{q\}\oplus\V\subseteq\Z\} 
+ \\
+&=\PP\{\{q\}\oplus(\V^\prime\cup(\V\setminus\V^\prime))\subseteq\Z\} \\
+&=\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} + \PP\{\{q\}\oplus(\V\setminus\V^\prime)\subseteq\Z\} \\
+&\geq\PP\{\{q\}\oplus\V^\prime\subseteq\Z\}\\ &=\vol(\V^\prime)\geq p.
 \end{split}\end{equation}
+\mbox{}\vspace{-0.5\baselineskip}
+\epf
 %
-\end{pf}
-%
+
 Notice that for polytopic $\Z$ and $\V^\prime$ the set $\Z\ominus\V^\prime$ can be computed explicitly and is itself polytopic.
@@
 %
-\begin{equation}\label{eq:alternative:MRPI:set}
-	X^\infty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+\begin{multline}\label{eq:alternative:MRPI:set}
+	X^\infty = \Bigl\{x\in\X: \\
+\begin{aligned} 
+&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i} \\
 &x_k\in\X\\
-	&(C+DK)x_k+v\in\Y\\
-	&\forall w_j\in\W,v\in \V^\prime,k\geq 0\end{aligned} \right\}
-\end{equation}
+&(C+DK)x_k+v\in\Y
+\end{aligned}\\
+\forall w_j\in\W,\ \forall v\in \V^\prime,\ \forall k\geq 0 \Bigr\}
+\end{multline}
+% \begin{multline}\label{eq:alternative:MRPI:set}
+% 	X^\infty = \Bigl\{x\in\X: \\
+% \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+% 	&x_k\in\X\\
+% 	&(C+DK)x_k+v\in\Y\\
+% 	&\forall w_j\in\W,\ \forall v\in \V^\prime,\ \forall k\geq 0 \Bigr\}
+% \end{aligned} 
+% \end{multline}
 %
@@
 %
-\begin{equation}
-	\X^\infty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+\begin{multline*}
+\X^\infty = \Bigl\{x\in\X: \\
+\begin{aligned}
+&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
 &x_k\in\X\\
-	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
-	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}
-\end{equation}
+&\PP\{(C+DK)x_k+v\in\Y\}\geq p 
+\end{aligned}\\
+\forall w_j\in\W,\, \forall k\geq 0 \Bigr\}
+\end{multline*}
+% \begin{equation}
+% 	\X^\infty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+% 	&x_k\in\X\\
+% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
+% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}
+% \end{equation}
 %
@@
 %
-\begin{equation}\begin{split}
+\begin{align*}
 	\D_k(X) &= (A+BK)^{k}X\oplus\W\oplus\dots\oplus(A+BK)^{k-1}\W\\
 	&= (A+BK)^k X\oplus \bigoplus_{i=0}^{k-1}(A+BK)^i\W
-\end{split}\end{equation}
+\end{align*}
 %
@@
 %
-\begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
-	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
-\end{equation}
+\begin{gather*}
+X^\infty = %\bigcap_{k\geq0}(A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) \\
+\bigcap_{k\geq0} \E_k, \\
+\E_k = (A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) .
+\end{gather*}
+% \begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
+% 	X^\infty = \bigcap_{k\geq0}\underbrace{(A+BK)^{-k}\left((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\right)}_{\E_k}.
+% \end{equation}
 %
@@
 
+\vspace{0.5\baselineskip}
 \begin{thm}
-Let $\Gamma$ be a map such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $((A+BK),\Gamma)$ be observable, then iteration~\eqref{eq:MRPI:sequence} terminates after a finite number of iterations~$N$, such that $X_{N+1}=X_N$ and $X_N=X^\infty$.
+Let $\Gamma$ be a map such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then iteration~\eqref{eq:MRPI:sequence} terminates after a finite number of iterations~$N$, such that $X_{N+1}=X_N$ and $X_N=X^\infty$.
 \end{thm}
 %
-\begin{pf}
+\bpf
 %
-The observability of $((A+BK),\Gamma)$ implies that $X_d$ is compact, since $X_{d-1}\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k}\X\subseteq\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1}\} = \{x:\pm\Gamma Ox\leq \bfa{1}\}$ for the observability matrix~$O$ which has full rank.
+The observability of $\bigl((A+BK),\Gamma\bigr)$ implies that $X_d$ is compact, since 
+\begin{align*}
+X_{d-1} 
+&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k}\X\\
+&\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
+& = \{x:\pm\Gamma \Obs x\leq \bfa{1}\}
+\end{align*}
+where $\Obs$ is the (full rank) observability matrix.
 
-Let~$P$ be such that $(A+BK)^TP(A+BK)\leq\rho^2P$ holds for $\rho$ denoting the spectral radius of $A+BK$.
+Let~$P$ be such that 
+\[
+(A+BK)^TP(A+BK) \leq \rho^2P
+\]
+holds, where $\rho$ denotes the spectral radius of $A+BK$.
 %
@@
 %
-\begin{equation}\begin{split}
-	&\bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
-	&\subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P(\sum_{i=0}^{k-1}\rho^i r)\subseteq\B_P(\frac{r}{1-\rho})
-\end{split}\end{equation}
+\begin{multline*}
+  \bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
+  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P(\sum_{i=0}^{k-1}\rho^i r)\subseteq\B_P(\frac{r}{1-\rho})
+\end{multline*}
 %
@@
 %
-\end{pf}
+\epf
 
@@
 %
-\begin{equation}
-	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+\begin{multline*}
+\C_n(\T) = \Bigl\{x\in\X: \\
+\begin{aligned}
+&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
 &x_N\in\T\\
 &x_k\in\X\\
-	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
-	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
-\end{equation}
+&\PP\{(C+DK)x_k+v\in\Y\}\geq p
+\end{aligned}\\
+\forall w_j\in\W,\, \forall k\geq 0 \Bigr\}	
+\end{multline*}
+% \begin{equation}
+% 	\C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+% 	&x_N\in\T\\
+% 	&x_k\in\X\\
+% 	&\PP\{(C+DK)x_k+v\in\Y\}\geq p\\
+% 	&\forall w_j\in\W,k\geq 0\end{aligned} \right\}	
+% \end{equation}
 %
@@
 %
-\begin{equation}
-	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+\begin{multline*}
+C_n(\T) = \Bigl\{ x\in\X: \\
+\begin{aligned}
+&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
 &x_N\in\T\\
 &x_k\in\X\\
-	&(C+DK)x_k+v\in\Y\\
-	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
-\end{equation}
+&(C+DK)x_k+v\in\Y
+\end{aligned}\\
+\forall w_j\in\W,\, \forall v\in \V^\prime,\, \forall k\in\{0,\dots,N\} \Bigr\}	
+\end{multline*}
+% \begin{equation}
+% 	C_n(\T) = \left\{x\in\X:\begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+% 	&x_N\in\T\\
+% 	&x_k\in\X\\
+% 	&(C+DK)x_k+v\in\Y\\
+% 	&\forall w_j\in\W,v\in \V^\prime,k\in\{0,\dots,N\}\end{aligned} \right\}	
+% \end{equation}
 %
@@
 
-In particular the one-step controllable set $C_1(\T)$ for $\T = \{x\in\RR^d:J_i x\leq1,i\leq M_\T\}$ is given by the projection of 
+In particular the one-step controllable set $C_1(\T)$ for 
+\[
+\T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
+\]
+is given by the projection of 
 %
-\begin{equation}
-	L_1(\T) = \left\{(x,u):\begin{aligned}
-	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
-	Ax+Bu+w\in\T\;\forall w\in\W
-	\end{aligned}\right\}
-\end{equation}
+\begin{multline*}
+L_1(\T) = \Bigl\{(x,u)\in (\X,\U): \\
+\begin{aligned}
+& Cx+Du + v\in\Y \\
+& Ax+Bu+w\in\T
+\end{aligned}\\
+\forall v\in\V^\prime,\, \forall w\in\W\Bigr\}
+%\end{aligned}
+\end{multline*}
+% \begin{equation}
+% 	L_1(\T) = \left\{(x,u):\begin{aligned}
+% 	x\in\X, u\in\U, Cx+Du + v\in\Y\;\forall v\in\V^\prime,\\
+% 	Ax+Bu+w\in\T\;\forall w\in\W
+% 	\end{aligned}\right\}
+% \end{equation}
 %
@@
 %
-For this we consider the class of parallelotopes (see e.g.~\cite{Coxeter:1973}), i.e. the minimal zonotope in $\RR^d$, $\spann(v_1,\dots,v_d) = \{x:\exists 0\leq t_i\leq1, x = \sum_{i=1}^d t_iv_i\}$.
+For this we consider the class of parallelotopes \citep[see
+e.g.][]{Coxeter:1973}), i.e.~the minimal zonotope in $\RR^d$: 
+\begin{multline*}
+  \spann(v_1,\dots,v_d) = \Bigl\{x:\exists t_i, \ 
+i = 1,\ldots, d, \\
+0 \leq t_i\leq1, \ 
+ x = \sum_{i=1}^dt_iv_i\Bigr\}.
+\end{multline*}
 %
@@
 \begin{equation}
-	\vol(\spann(v_1,\dots,v_d)) = \abs{\det(v_1,\dots,v_d)}.
+	\vol\Bigl(\spann(v_1,\dots,v_d)\Bigr) = \abs{\det(v_1,\dots,v_d)}.
 \end{equation}
 %
-Recall that $\det(\lambda v_1,\dots,v_d) = \lambda\det(v_1,\dots,v_d)$, therefore we have that for fixed $v_1,\dots,v_d$ the volume of $\spann(t_1v_1,\dots,t_dv_d)$ with $0<t_i\leq1$ is given by
+Recall that 
+\[
+\det(\lambda v_1,\dots,v_d) = \lambda\det(v_1,\dots,v_d),
+\]
+therefore we have that for fixed $v_1,\dots,v_d$ the volume of $\spann(t_1v_1,\dots,t_dv_d)$ with $0<t_i\leq1$ is given by
 %
 \begin{equation}
-	\vol(\spann(t_1v_1,\dots,t_dv_d)) = \abs{\det(v_1,\dots,v_d)}\prod_{i=1}^d t_i
+	\vol\Bigl(\spann(t_1v_1,\dots,t_dv_d)\Bigr) = \abs{\det(v_1,\dots,v_d)}\prod_{i=1}^d t_i
 \end{equation}
@@
 It is known that the volume of an object is translation invariant, i.e. 
-$\vol(\spann(t_1v_1,\dots,t_dv_d)\oplus\{v_0\}) = \vol(\spann(t_1v_1+v_0,\dots,t_dv_d+v_0)) = \vol(\spann(t_1v_1,\dots,t_dv_d))$.
-
+\begin{multline*}
+\vol\Bigl(\spann(t_1v_1,\dots,t_dv_d)\oplus\{v_0\}\Bigr) \\
+= \vol\Bigl(\spann(t_1v_1+v_0,\dots,t_dv_d+v_0)\Bigr) \\
+= \vol\Bigl(\spann(t_1v_1,\dots,t_dv_d)\Bigr).
+\end{multline*}
 By using $v_0$ and $t_i$ as decision variables we can solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract} by solving an optimisation program with $2d$ decision variables.
@@
 \begin{equation}
-	\V^\prime = \underset{i\leq 2^d}{\conv}\{(t_1v_1,\dots,t_dv_d)\lambda_i+v_0\}
+	\V^\prime = \underset{i\leq 2^d}{\conv}\Bigl\{(t_1v_1,\dots,t_dv_d)\lambda_i+v_0\Bigr\}
 \end{equation}
@@
 \begin{equation}\label{eq:containment:linear:1}
-	\Gamma((t_1v_1,\dots,t_dv_d)\lambda_i+v_0)\leq \bfa{1}, i\leq 2^d \Leftrightarrow \V^\prime\subseteq\V
+	\Gamma\Bigl( (t_1v_1,\dots,t_dv_d)\lambda_i+v_0\Bigr)\leq \bfa{1}, \ i\leq 2^d 
+%\Leftrightarrow \V^\prime\subseteq\V
 \end{equation}
 %
-\begin{equation}
-	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} \Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
+\begin{equation}\label{eq:measure:p:1}
+	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} 
+%\Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
 \end{equation}
@@
 \begin{equation}\label{eq:linear:inequalites:on:t:1}
-	0<t_i\leq1, i\leq d
+	0<t_i\leq1, \ i\leq d .
 \end{equation}
@@
 %
-analogous for~\eqref{seq:optimisation:n:step:set:abstract}
+
+Analogously, \eqref{seq:optimisation:n:step:set:abstract} can be restated as
 %
@@
 \begin{equation}\label{eq:containment:linear:2}
-	\Gamma((t_1v_1,\dots,t_dv_d)\lambda_i+v_0)\leq \bfa{1}, i\leq 2^d \Leftrightarrow \V^\prime\subseteq\V
+	\Gamma\Bigl( (t_1v_1,\dots,t_dv_d)\lambda_i+v_0\Bigr)\leq \bfa{1}, \ i\leq 2^d 
+%\Leftrightarrow \V^\prime\subseteq\V
 \end{equation}
 %
-\begin{equation}
-	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} \Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
+\begin{equation}\label{eq:measure:p:2}
+	\prod_{i=1}^d t_i\geq p \frac{\vol(\V)}{\abs{\det(v_1,\dots,v_d)}} 
+%\Leftrightarrow \frac{\vol(\V^\prime)}{\vol(\V)}\geq p
 \end{equation}
@@
 \begin{equation}\label{eq:linear:inequalites:on:t:2}
-	0<t_i\leq1, i\leq d
+	0<t_i\leq1, \ i\leq d.
 \end{equation}
@@
 %
-Notice that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq const.$ is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+%
+Note also that the constraints (\ref{eq:containment:linear:1}) and (\ref{eq:containment:linear:2}) are equivalent to
+\[
+\V^\prime\subseteq\V ,
+\]
+whereas the constraints (\ref{eq:measure:p:1}) and (\ref{eq:measure:p:2}) are equivalent to
+\[
+\frac{\vol(\V^\prime)}{\vol(\V)}\geq p.
+\]
 %
@@
 %
-subject to the constraints $\X = \{x:\norm{x}_\infty\leq15\}$, $\U = \{u:\abs{u}\leq2\}$ and $\W=\{w:\norm{w}_1\leq1\}$.
+subject to the constraints 
+\begin{align*}
+\X &= \{x:\norm{x}_\infty\leq15\}, \\
+\U &= \{u:\abs{u}\leq2\}, \\
+\W &= \{w:\norm{w}_1\leq1\}.
+\end{align*}
 %
@@
 $$
-\V = \conv\{\begin{pmatrix}\pm0.08\\0\end{pmatrix},\begin{pmatrix}0\\\pm0.07\end{pmatrix}\}.
+\V = \conv\biggl\{\begin{pmatrix}\pm0.08\\0\end{pmatrix},\begin{pmatrix}0\\\pm0.07\end{pmatrix}\biggr\}.
 $$
@@
 %
-As span vectors we use $v_1 = (0.07,0.08)^T$ and $v_2 = (-0.07,0.08)^T$, which means that $\V^\prime$ is a scaled version of $\V$.
+As span vectors we use 
+\[
+v_1 = \begin{pmatrix} 0.07 \\ 0.08\end{pmatrix} \quad \text{and}\quad 
+v_2 = \begin{pmatrix}-0.07 \\ 0.08\end{pmatrix},
+\] 
+which means that $\V^\prime$ is a scaled version of $\V$.
 %
@@
 %
-\begin{equation}\label{eq:comparison:set}\begin{split}
-	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
-	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
-\end{split}\end{equation}
+\begin{subequations}\label{eq:comparison:set}
+\begin{equation}\min_{\gamma_1,\dots,\gamma_4} \  \ \sum_{i=1}^4\gamma_i
+\end{equation}
+subject to 
+\begin{equation}
+\Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\dots,4\}
+\end{equation}
+\end{subequations}
+% \begin{equation}\label{eq:comparison:set}\begin{split}
+% 	\min_{\gamma_1,\dots,\gamma_4}&\quad\sum_{i=1}^4\gamma_i\\
+% 	\text{s.t.}&\quad \Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,i\in\{1,\dots,4\}
+% \end{split}\end{equation}
 %
@@
 %
+
 \begin{figure}
@@
 \label{fig:MRPI:optimised}
-\end{figure}
+\vspace{4mm}\end{figure}
 
@@
 \label{fig:n:step:controllable:set}
-\end{figure}
+\vspace{4mm}\end{figure}
 
@@
 
-\bibliographystyle{alpha}
+%\bibliographystyle{alpha}
 \bibliography{MyBibliography}

### 2016-11-05 draft.tex
edits 2.1

@@
 \providecommand{\E}{\mathcal E}
+\providecommand{\F}{\mathscr F}
 \providecommand{\W}{\mathcal W}
@@
 
-%\allowdisplaybreaks[1]
+\allowdisplaybreaks[4]
 
@@
 This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to chance constraints.
-The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints; in contrast existing methods based on random sampling are only able to satisfy such constraints with a certain level of confidence.
+The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints.
+In contrast, existing methods based on random sampling are only able to satisfy such constraints with a certain level of confidence.
 The proposed approach uses explicitly parametrised auxiliary disturbance sets, which are optimised so as to maximise the relevant positively invariant or $n$-step controllable set.
@@
 
-The following notation is employed: $A\oplus B = \{x:x=a+b,\, a\in A,\, b\in B\}$ denotes the Minkowski addition, $A\ominus B = \{x: x+b \in A \, \forall b\in B\}$ the Pontryagin difference, for a real set $C\subset\RR^d$ we denote the image of $C$ under the linear map $A:\RR^d\rightarrow\RR^d$ by $AC = \{y\in\RR^d:Ax=y,x\in C\}$ and the pre-image $A^{-1}C = \{y\in\RR^d:Ay\in C\}$.
+\textit{Notation.} Given sets $A,B\subset\RR^d$, $A\oplus B = \{x:x=a+b,\, a\in A,\, b\in B\}$ denotes the Minkowski sum and $A\ominus B = \{x: x+b \in A \ \forall b\in B\}$ the Pontryagin difference.
+We denote the image and pre-image of $C\subset\RR^d$ under the linear map $A:\RR^d\rightarrow\RR^d$ respectively as $AC = \{y\in\RR^d:Ax=y,\, x\in C\}$ and $A^{-1}C = \{y\in\RR^d:Ay\in C\}$.
+The $d$-dimensional volume of $C\subset\RR^d$ is denoted by $\vol(C)$.
 %
-We denote the probability of an event $E$ by $\PP\{E\}$, throughout this paper we assume the probability density to be uniform.
+We define $v$ as a random parameter on a probability space $(\V,\F,\PP)$ and denote the probability of an event $E(v)$ as $\PP\{v\in\V : E(v)\}$.
+%; throughout this paper the probability density of $v$ is assumed to be uniform.
 %
-The set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball of radius $r$ centred at the origin, for a matrix $\Gamma\in\RR^{m\times n}$ the notation $\Gamma x\leq \bfa{1}$ is to be understood element-wise, where $\bfa{1}$ is a vector of ones in $\RR^m$.
+The set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball of radius $r$ centred at the origin.
+For a matrix $\Gamma\in\RR^{m\times n}$ the notation $\Gamma x\leq \bfa{1}$ is to be understood element-wise, where $\bfa{1}$ is a vector of ones in $\RR^m$.
 
@@
 %
-\begin{equation}
-	x^+ = Ax + Bu + w
+\begin{equation}\label{eq:system}
+	x^+ = Ax + Bu + w ,
 \end{equation}
 %
-with state $x$ and control input $u$ subject to the constraints 
-\begin{align*}
-&x \in\X = \bigl\{x\in\RR^d : E_ix\leq 1, \ i\leq M_\X\bigr\}, \\
-&u\in\U = \bigl\{u\in\RR^{q_\U} : F_i u\leq 1, \ i\leq M_\U\bigr\},
-\end{align*} 
-and with disturbance input $w$ subject to the constraints
-\[
-w\in\W = \bigl\{w\in\RR^{q_\W}:G_i w\leq 1,\ i\leq M_\W \bigr\}.
-\]
-%
-We furthermore consider the auxiliary output variable 
-%
-\begin{equation}
-	y = Cx + Du + v
+where the state $x$ and control input $u$ are subject to constraints defined in terms of compact, convex polytopic sets $\X$, $\U$:
+\begin{equation}\label{eq:state_input:constraints}
+\begin{aligned}
+&x \in\X = \bigl\{x\in\RR^d : E_ix\leq 1, \, i\leq M_\X\bigr\}, \\
+&u\in\U = \bigl\{u\in\RR^{q_\U} : F_i u\leq 1, \, i\leq M_\U\bigr\},
+\end{aligned}
+\end{equation} 
+and the disturbance input $w$ is subject to the constraint
+\begin{equation}\label{eq:disturbance}
+w\in\W = \bigl\{w\in\RR^{q_\W}:G_i w\leq 1,\, i\leq M_\W \bigr\}.
 \end{equation}
 %
-which depends on a random variable $v$:
+We furthermore consider the output variable $y$,
+%
+\[%\begin{equation}\label{eq:output}
+	y = Cx + Du + v
+\]%\end{equation}
+%
+which depends on the random variable $v$,
 \[
-v\in\V = \bigl\{v\in\RR^{q_\Y}:\Gamma_i v\leq 1, \ i\in M_\V\bigr\},
+v\in\V = \bigl\{v\in\RR^{q_\Y}:\Gamma_i v\leq 1, \ i\in M_\V\bigr\}. 
 \]
-for which the probability distribution is assumed to be uniform.
+Throughout this paper $v$ is assumed to be uniformly distributed on $\V$.
+%Throughout this paper the probability density function of $v$ is assumed to be uniform.
 %
-The output is probabilistically constrained to satisfy
+The output variable $y$ is subject to the chance (or probabilistic) constraint
 %
 \begin{equation}\label{eq:probabilistic:constraint}
-	\PP\bigl\{ v \in \mathcal{V} : y = Cx + Du + v \in \mathcal{Y} \bigr\}\geq p.
+	\PP\bigl\{ v \in \mathcal{V} : y = Cx + Du + v \in \mathcal{Y} \bigr\}\geq p
 \end{equation}
 %
-with
+for given $p\in(0,1]$, with
 \[
@@
 
-\vspace{0.5\baselineskip}\begin{prop}
-Let $v\in\V$ be a uniformly distributed random variable, let $\V^\prime\subseteq\V$ such that $\vol(\V^\prime)\geq p$, then every $q\in\Z\ominus\V^\prime$ satisfies $\PP\{q+v\in\Z\}\geq p$.
+\vspace{0.5\baselineskip}
+\begin{prop}\label{prop1}
+Let $v\in\V$ be a uniformly distributed random variable and let $\V^\prime\subseteq\V$ be such that $\vol(\V^\prime)\geq p$, then every $q\in\Z\ominus\V^\prime$ satisfies $\PP\{v\in\V : q+v\in\Z\}\geq p$.
 \end{prop}
 %
+
 \bpf
 %
-Using the fact that $\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} = \PP\{\V^\prime\} = \vol(\V^\prime)$ for all $q\in\Z\ominus\V^\prime$ we have
-%
-\begin{equation}\begin{split}
-&\PP\{q+v\in\Z\} = \PP\{\{q\}\oplus\V\subseteq\Z\} 
- \\
-&=\PP\{\{q\}\oplus(\V^\prime\cup(\V\setminus\V^\prime))\subseteq\Z\} \\
-&=\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} + \PP\{\{q\}\oplus(\V\setminus\V^\prime)\subseteq\Z\} \\
-&\geq\PP\{\{q\}\oplus\V^\prime\subseteq\Z\}\\ &=\vol(\V^\prime)\geq p.
-\end{split}\end{equation}
-\mbox{}\vspace{-0.5\baselineskip}
+For any given $q\in\Z\ominus\V^\prime$, the definition of the Pontryagin difference implies that
+\[
+q+v\in\Z \quad \text{whenever} \quad  v\in\V^\prime.
+\]
+Therefore, for every $q\in\Z\ominus\V^\prime$, the probability of the event that $q+v$ lies in $\Z$ can be no less than the probability of the event that $v$ lies in $\V^\prime$. It follows that 
+\[
+\PP\{ v\in\V : q + v\in \Z\} \geq \PP\{\V^\prime\} = \vol(\V^\prime)
+\]
+and hence $\PP\{ v\in\V : q + v\in \Z\} \geq p$ if $\V^\prime$ is such that $\vol(\V^\prime) \geq p$.
+% Using the fact that $\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} = \PP\{\V^\prime\} = \vol(\V^\prime)$ for all $q\in\Z\ominus\V^\prime$ we have
+% %
+% \begin{align*}
+% &\PP\{v\in\V : q+v\in\Z\} 
+% =\PP\{v\in \V^\prime\cup(\V\setminus\V^\prime) : q + v \in \Z, \ ()\subseteq\Z\} \\
+% &=\PP\{\{q\}\oplus\V^\prime\subseteq\Z\} + \PP\{\{q\}\oplus(\V\setminus\V^\prime)\subseteq\Z\} \\
+% &\geq\PP\{\{q\}\oplus\V^\prime\subseteq\Z\}\\ &=\vol(\V^\prime)\geq p. 
+% \end{align*}
+%\mbox{}\vspace{-0.5\baselineskip}
 \epf
@@
 
-Notice that for polytopic $\Z$ and $\V^\prime$ the set $\Z\ominus\V^\prime$ can be computed explicitly and is itself polytopic.
+Note that for polytopic $\Z$ and $\V^\prime$ the set $\Z\ominus\V^\prime$ can be computed explicitly and is itself polytopic.
 
-In the sequel of this paper we discuss how~$\V^\prime$ can be chosen in order to obtain the largest guaranteed n-step controllable set for a given target set, guaranteed positive invariant set.
+In the remainder of this paper we discuss how~$\V^\prime$ can be chosen in order to obtain the largest guaranteed $n$-step controllable set for a given target set and the largest guaranteed positively invariant set for the system (\ref{eq:system}) subject to the robust constraints~(\ref{eq:state_input:constraints}) and the chance constraint (\ref{eq:probabilistic:constraint}).
 
@@
 %
-First we discuss how we can extend existing methods to calculate the maximal robust positive invariant (MRPI) set (see e.g.~\cite{blanchini:2007}) in such a way that all states produce only feasible successor states for a given feedback controller $u = Kx$.
+First we discuss how to extend existing methods to calculate the maximal robust positively invariant (MRPI) set (see e.g.~\cite{blanchini:2007}) in such a way that all states in the MRPI set produce only feasible successor states for a given feedback controller $u = Kx$.
 %
-I.e. an invariant set for which all possible trajectories satisfy state constraints and probabilistic constraint at all time.
+Thus we seek to determine a set of initial conditions for which all possible trajectories of (\ref{eq:system}) subject to (\ref{eq:disturbance}) satisfy the robust constraints~(\ref{eq:state_input:constraints}) and probabilistic constraint (\ref{eq:probabilistic:constraint}).
+Denoting the largest such set as $\X^\infty$ we have
+\begin{multline*}
+\X^\infty = \Bigl\{x\in\X: \\
+\begin{aligned}
+&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i}\\
+&x_k\in\X\\
+&Kx_k\in\U\\
+&\PP\{v\in\V : (C+DK)x_k+v\in\Y\}\geq p 
+\end{aligned}\\
+\forall w_k\in\W,\, \forall k\geq 0 \Bigr\} .
+\end{multline*}
 %
-\begin{multline}\label{eq:alternative:MRPI:set}
-	X^\infty = \Bigl\{x\in\X: \\
-\begin{aligned} 
-&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i} \\
-&x_k\in\X\\
-&(C+DK)x_k+v\in\Y
-\end{aligned}\\
-\forall w_j\in\W,\ \forall v\in \V^\prime,\ \forall k\geq 0 \Bigr\}
-\end{multline}
 % \begin{multline}\label{eq:alternative:MRPI:set}
@@
 %
-It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\X^\infty$:
+% It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\X^\infty$:
+For a given set $\V^\prime$, let $X^\infty$ denote the set
 %
-\begin{multline*}
-\X^\infty = \Bigl\{x\in\X: \\
+\begin{multline}\label{eq:alternative:MRPI:set}
+	X^\infty = \Bigl\{x\in\X: \\
 \begin{aligned} 
-&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
-&x_k\in\X\\
-&\PP\{(C+DK)x_k+v\in\Y\}\geq p 
+&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i} \\
+&x_k\in\X \\ 
+&Kx_k\in\U \\
+&(C+DK)x_k+v_k\in\Y
 \end{aligned}\\
-\forall w_j\in\W,\, \forall k\geq 0 \Bigr\}
-\end{multline*}
+\forall w_k\in\W,\ \forall v_k\in \V^\prime,\ \forall k\geq 0 \Bigr\} .
+\end{multline}
 % \begin{equation}
@@
 %
-The inclusion $X^\infty\subseteq\X^\infty$ holds for any $\V^\prime\subseteq\V$ with the appropriate probability measure, therefore maximising the volume of $X^\infty$ improves the approximation of $\X^\infty$.
+Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\X^\infty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
+Furthermore, by maximising the volume of $X^\infty$, we can improve the approximation of $\X^\infty$.
 
-In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions met in~\eqref{eq:alternative:MRPI:set} we introduce the set of all possible successor states~$\D_k(X)$ of states in $X$ at time $k$:
+In order to determine an algorithm to compute $X^\infty$ we rewrite the conditions in~\eqref{eq:alternative:MRPI:set} by introducing the set of all possible successor states~$\D_k(X)$ of states in $X$ after $k$ time steps:
 %
@@
 %
-Using $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate condition~\eqref{eq:alternative:MRPI:set} to
+Defining $\R = (C+DK)^{-1}(\Y\ominus\V^\prime)$ we can abbreviate the conditions defining $X^\infty$ in~\eqref{eq:alternative:MRPI:set} to
 %
@@
 %
-With this identity we can determine a direct way of determining $X^\infty$:
+Using these conditions we can express $X^\infty$ directly as
 %
-\begin{gather*}
+\begin{gather}
 X^\infty = %\bigcap_{k\geq0}(A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) \\
 \bigcap_{k\geq0} \E_k, \\
-\E_k = (A+BK)^{-k}\Bigl((\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\Bigr) .
-\end{gather*}
+\E_k = (A+BK)^{-k}\biggl[(\X\cap\R)\ominus\bigoplus_{i=0}^{k-1}(A+BK)^i\W\biggr] . \label{eq:Ek:subtract}
+\end{gather}
 % \begin{equation}\label{eq:direct:formulation:MRPI:with:intersection}
@@
 %
-Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore using available methods it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined.
+Due to its definition~$\E_k$ satisfies $\D_k(\E_k)\subseteq\X\cap\R$ for each $k\geq0$, furthermore it can be shown that $\E_k$ expands exponentially and therefore $X^\infty$ is finitely determined  (see Theorem~\ref{thm2} below).
 %
-In order to computationally determine $X^\infty$ we define the recursive sequence
+In order to compute $X^\infty$ we define the sequence $X_0,X_1,\ldots$ via the iteration:
 %
 \begin{equation}\label{eq:MRPI:sequence}
-	\begin{split}
-	X_0 &= \X\\
-	Z_k &= X_k\cap\R\\
-	X_{k+1} &= Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
-	\end{split}
+\begin{aligned}
+  & X_0 = \X \\
+  & \begin{aligned}
+      & Z_k = X_k\cap\R\\
+      & X_{k+1} = Z_k\cap(A+BK)^{-1}(Z_k\ominus\W)
+    \end{aligned} 
+  \ \Biggr\} \ \ k = 1,2,\ldots
+\end{aligned}
 \end{equation}
 %
-Notice that $X_k = \bigcap_{l\leq k}\E_l$ and therefore the recursion terminates, analogue to the conventional MRPI calculation, once $X_k\subseteq X_{k+1}$.
+%with $X_0= \X$.
+Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ once $X_k\subseteq X_{k+1}$.
 
 \vspace{0.5\baselineskip}
-\begin{thm}
-Let $\Gamma$ be a map such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then iteration~\eqref{eq:MRPI:sequence} terminates after a finite number of iterations~$N$, such that $X_{N+1}=X_N$ and $X_N=X^\infty$.
+\begin{thm}\label{thm2}
+Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that
+yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
 \end{thm}
@@
 %
-The observability of $\bigl((A+BK),\Gamma\bigr)$ implies that $X_d$ is compact, since 
+The observability of the pair $\bigl((A+BK),\Gamma\bigr)$ implies that $X_{d-1}$ is compact, since 
 \begin{align*}
@@
 &\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
-& = \{x:\pm\Gamma \Obs x\leq \bfa{1}\}
+& = \bigl\{x:\pm\Gamma \Obs x\leq \bfa{1}\bigr\}
 \end{align*}
@@
   \bigoplus_{i=0}^{k-1}(A+BK)^i\W \subseteq \bigoplus_{i=0}^{k-1}(A+BK)^i\B_P(r)\\
-  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P(\sum_{i=0}^{k-1}\rho^i r)\subseteq\B_P(\frac{r}{1-\rho})
+  \subseteq\bigoplus_{i=0}^{k-1}\B_P(\rho^i r) = \B_P\biggl(\sum_{i=0}^{k-1}\rho^i r\biggr)\subseteq\B_P\Bigl(\frac{r}{1-\rho}\Bigr) .
 \end{multline*}
 %
-i.e. $\E_k$ consists of an expanding minuend and a bounded subtrahend.
+It follows that the subtrahend in square brackets on the RHS of (\ref{eq:Ek:subtract}) is bounded for all $k$ by $\B_P\bigl(r / (1-\rho)\bigr)$.
+%It follows that the RHS of (\ref{eq:Ek:subtract}) consists of an expanding minuend and a bounded subtrahend.
 %
-Therefore $\E_k$ expands exponentially, since $X_{d-1}$ is bounded there exists an integer~$N$ such that $X_{N}\cap\E_{N+1}=X_N$ hence $X_N=X^\infty$.
+Therefore 
+%$\E_k$ expands exponentially. Hence 
+the iteration (\ref{eq:MRPI:sequence}) must either yield $X_N = \emptyset$ for finite $N$
+(in which case $X^\infty=\emptyset$) or,
+since $X_{d-1}$ is bounded and $\E_k$ expands exponentially, there must exist a finite $N$ such that $X_{N}\cap\E_{N+1}=X_N$ and hence $X_N=X^\infty$.
 %
@@
 
-The optimisation program to approximate the positive invariant set $\X^\infty$ can therefore be formulated as
+An optimisation program to approximate the positively invariant set $\X^\infty$ can therefore be formulated as
 %
@@
 %
-In section~\ref{sec:volume:of:hypercube} we will discuss how an optimisation can be solved using parallelotopes for~$\V^\prime$.
+In section~\ref{sec:volume:of:hypercube} we discuss how this optimisation can be solved using parallelotopes for~$\V^\prime$.
 
-\subsection{Approximating the n-step controllable set}\label{ssec:approximating:n:step}
+\subsection{Approximating the $n$-step controllable set}\label{ssec:approximating:n:step}
 %
-We now turn our attention to the n-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
+We now turn our attention to the $n$-step controllable set~$\C_n(\T)$ for a given target set~$\T$.
 %
-That is the set of all states such that a sequence of admissible inputs exists that takes any state $x\in\C_n$ to the target set $x_n\in\T$ for any admissible disturbance sequence $w\in\W$ while guaranteeing state- and probabilistic constraint satisfaction.
+That is the set of initial conditions $x_0\in\C_n$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
+$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
 %
@@
 \begin{multline*}
-\C_n(\T) = \Bigl\{x\in\X: \\
+\C_n(\T) = \Bigl\{x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
 \begin{aligned}
-&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
-&x_N\in\T\\
+&x_k = A^k x_0 + \sum_{i=1}^{k} A^{k-i}B u_{k-i}(x_{k-i}) + \sum_{i=1}^{k} A^{k-i} w_{k-i}\\
+&x_n\in\T\\
 &x_k\in\X\\
-&\PP\{(C+DK)x_k+v\in\Y\}\geq p
+&u_k(x_k)\in\U\\
+&\PP\bigl\{v\in\V : Cx_k + Du_k(x_k) +v \in\Y\bigr\}\geq p
 \end{aligned}\\
-\forall w_j\in\W,\, \forall k\geq 0 \Bigr\}	
+\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n\} \Bigr\}	
 \end{multline*}
@@
 %
-Again, it is trivial to see that the set
+Again, it is easy to verify that the set
 %
 \begin{multline*}
-C_n(\T) = \Bigl\{ x\in\X: \\
+C_n(\T) = \Bigl\{ x\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
 \begin{aligned}
-&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+&x_k = A^k x_0 + \sum_{i=1}^{k} A^{k-i}B u_{k-i}(x_{k-i}) + \sum_{i=1}^{k} A^{k-i} w_{k-i}\\
 &x_N\in\T\\
 &x_k\in\X\\
-&(C+DK)x_k+v\in\Y
+&u_k(x_k)\in\U \\
+&Cx_k+Du_k(x_k) + v_k \in\Y
 \end{aligned}\\
-\forall w_j\in\W,\, \forall v\in \V^\prime,\, \forall k\in\{0,\dots,N\} \Bigr\}	
+\forall w_j\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n\} \Bigr\}	
 \end{multline*}
@@
 %
-is always contained in $\C_n$ for any admissible choice of $\V^\prime\subseteq\V$.
+is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with measure $\PP\{\V^\prime\} \geq p$.
 %
-As in the case of the positive invariant set, fixing $\V^\prime$ to be polytopic leads to a computationally tractable algorithm yielding~$C_n$ to be a polytopic approximation of~$\C_n$, and optimising over~$\V^\prime$ to maximise the volume of~$C_n$ indirectly improves the approximation of $\C_n$.
+As in the case of the positively invariant set, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$.
+This suggests an algorithm for constructing $C_n$ as a polytopic approximation of~$\C_n$ by optimising~$\V^\prime$ so as to maximise the volume of~$C_n$.
+% indirectly improves the approximation of $\C_n$.
 %
-It is known that $C_n(\T) = C^n_1(\T) = C_1(C_1(\dots C_1(\T)\dots))$ (see e.g.~\cite{blanchini:2007}), which allows the use of simple computational geometry algorithms.
+It is known that 
+%$C_n(\T) = C^n_1(\T) \doteq C_1(C_1(\cdots C_1(\T)\cdots))$ 
+$C_n(\T) = C^n_1(\T) \doteq C_1 \circ C_1 \circ \cdots \circ C_1(\T)$ 
+\citep[see e.g.][]{blanchini:2007}, which allows the use of simple computational geometry algorithms.
 
@@
 
-The optimisation approximating the n-step controllable set $\C_n(\T)$ is then given as
+The optimisation approximating the $n$-step controllable set $\C_n(\T)$ is then given as
 %
@@
 %
-To achieve the best possible performance while guaranteeing constraint satisfaction a closed loop min-max model predictive control problem would be formulated, see e.g.~\cite{Lee:1997}.
+To achieve the best possible performance while guaranteeing constraint satisfaction a closed loop min-max model predictive control problem should be formulated, see e.g.~\cite{Lee:1997}.
 %
@@
 %
-So that if a chance constrained model predictive control problem is reformulated as a deterministically constrained problem guaranteeing probabilistic feasibility, the sets $C_n(\T)$ would play the role of stage constraints with the target set $\T=X^\infty$ to guarantee recursive feasibility.
+Therefore to reformulate a chance constrained model predictive control problem as a deterministically constrained problem with guaranteed probabilistic feasibility and guaranteed recursive feasibility, the sets $C_n(\T)$ can be introduced as stage constraints, and the target set $\T$ can be chosen as the robust positively invariant set $X^\infty$.
 \end{rem}
@@
 %
-In this section we present a method allowing us to optimise over polytopes as required to solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract}.
+In this section we present a method that enables optimisation over polytopes, as is required to solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract}.
 %
@@
 \[
-\det(\lambda v_1,\dots,v_d) = \lambda\det(v_1,\dots,v_d),
+\det(\lambda v_1,v_2,\dots,v_d) = \lambda\det(v_1,\dots,v_d),
 \]
@@
 %
-First we illustrate the approximation of the guaranteed positive invariant set~$X^\infty$ for the system
+First we illustrate the approximation of the guaranteed positively invariant set~$X^\infty$ for the system
 %
@@
 \includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
-\caption{The guaranteed positive invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the robust positive invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
+\caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
 \label{fig:MRPI:optimised}
@@
 %
-In this paper we presented a method in which the positive invariant set and the n-step controllable set of a stochastically constrained system are approximated respectively.
+In this paper we presented a method in which the positively invariant set and the $n$-step controllable set of a stochastically constrained system are approximated respectively.
 %
@@
 %
-Although the presented scheme scales well to higher dimensions, the complexity of positive invariant sets and n-step controllable sets does not.
+Although the presented scheme scales well to higher dimensions, the complexity of positively invariant sets and $n$-step controllable sets does not.
 %
@@
 %
-An additional improvement to the n-step controllable set $C_n(\T)$ could be obtained by introducing $\V_1^\prime,\dots,\V_{n-1}^\prime$, to allow different sets $\V_i^\prime$ at each stage introducing $(n-1)\times 2d$ additional decision variables.
+An additional improvement to the $n$-step controllable set $C_n(\T)$ could be obtained by introducing $\V_1^\prime,\dots,\V_{n-1}^\prime$, to allow different sets $\V_i^\prime$ at each stage introducing $(n-1)\times 2d$ additional decision variables.
 

### 2016-11-06 draft.tex
edits 3

@@
 \providecommand{\B}{\mathcal B}
-\providecommand{\C}{\mathcal C}
+\providecommand{\C}{\mathscr C}
+\providecommand{\Xinfty}{{\mathscr X}^\infty}
 \providecommand{\E}{\mathcal E}
@@
 
-\title{Maximising the guaranteed feasible set for uncertain MPC schemes with probabilistic constraints}%\thanksref{footnoteinfo}} 
+\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
 % Title, preferably not more than 10 words.
@@
 This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to chance constraints.
-The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints.
-In contrast, existing methods based on random sampling are only able to satisfy such constraints with a certain level of confidence.
-The proposed approach uses explicitly parametrised auxiliary disturbance sets, which are optimised so as to maximise the relevant positively invariant or $n$-step controllable set.
+The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints of the control problem.
+In contrast, existing methods based on random sampling are only able to satisfy such constraints with a fixed level of confidence.
+The proposed approach uses explicitly parametrised auxiliary disturbance sets, which are optimised subject to a constraint on their probability measure so as to maximise the relevant positively invariant or $n$-step controllable set.
 The results are illustrated by numerical examples.
@@
 %In addition to pure analysis purposes, 
-these sets are often used as terminal constraint sets model predictive control in order to guarantee the feasibility of the control scheme at all times \citep[see e.g.][]{Mayne2014}.
+these sets are often used as terminal constraint sets in Model Predictive Control (MPC) in order to guarantee the feasibility of the control scheme at all times \citep[see e.g.][]{Mayne2014}.
 %
@@
 %
-However, for simple probability distributions, this approach does not require sampling; instead we can explicitly parametrise an auxiliary disturbance set in which all probabilistic conditions are met.
+However, for simple probability distributions such as the uniform distribution considered in this paper, this approach does not require sampling; instead we can explicitly parametrise an auxiliary disturbance set in which all probabilistic conditions are met.
 %
@@
 
-In order to formulate a robust model predictive control law for a chance constrained stochastic system while introducing a minimal amount of conservatism, we consider a closed-loop min-max formulation~\citep{Lee:1997}.
+In order to formulate a robust MPC law for a chance constrained stochastic system while introducing a minimal amount of conservatism, we consider a closed-loop min-max formulation~\citep{Lee:1997}.
 This requires the determination of additional constraints.
@@
 This paper is organised  as follows:
-In section~\ref{sec:setup} we present the considered problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, the conditions for the positively invariant set under chance constraints.
-The corresponding conditions for the $n$-step controllable set are derived in section~\ref{ssec:approximating:n:step}.
+In section~\ref{sec:setup} we present the problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, conditions that define the positively invariant set under chance constraints.
+The corresponding conditions for the $n$-step controllable set are derived in section~\ref{ssec:approximating:n:step} and these are used to define an MPC law in section~\ref{ssec:mpc}.
 %
@@
 %
-The set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball of radius $r$ centred at the origin.
-For a matrix $\Gamma\in\RR^{m\times n}$ the notation $\Gamma x\leq \bfa{1}$ is to be understood element-wise, where $\bfa{1}$ is a vector of ones in $\RR^m$.
+For a positive definite matrix $P$ we write $\|x\|_P^2 = x^TPx$, and the set $\B_P(r) = \{x\in\RR^d:x^TPx\leq r^2\}$ denotes the $P$-ball of radius $r$ centred at the origin.
+The constraint $\Gamma x\leq \bfa{1}$, where $\Gamma\in\RR^{m\times n}$ and $\bfa{1}$ is a vector of ones in $\RR^m$, is understood to apply element-wise.
 
@@
 
-\subsection{Approximating the guaranteed invariant set}\label{ssec:approximating:MRPI}
+\section{Approximating the guaranteed invariant set}\label{ssec:approximating:MRPI}
 %
@@
 Thus we seek to determine a set of initial conditions for which all possible trajectories of (\ref{eq:system}) subject to (\ref{eq:disturbance}) satisfy the robust constraints~(\ref{eq:state_input:constraints}) and probabilistic constraint (\ref{eq:probabilistic:constraint}).
-Denoting the largest such set as $\X^\infty$ we have
+Denoting the largest such set as $\Xinfty$ we have
 \begin{multline*}
-\X^\infty = \Bigl\{x\in\X: \\
+\Xinfty = \Bigl\{x_0\in\X: \\
 \begin{aligned}
-&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i}\\
-&x_k\in\X\\
+% &x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i}\\
+% &x_{k+1} = (A+BK)^{k+1} x + \sum_{i=1}^{k+1} (A+BK)^{k+1-i} w_{k+1-i}\\
+&x_{k+1} = (A+BK)^{k+1} x_0 + \sum_{i=0}^{k} (A+BK)^{k-i} w_{i}\\
+&x_{k+1}\in\X\\
 &Kx_k\in\U\\
@@
 %
-% It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\X^\infty$:
+% It is obvious that $X^\infty$ contained in the invariant set of the original problem~$\Xinfty$:
 For a given set $\V^\prime$, let $X^\infty$ denote the set
@@
 \begin{multline}\label{eq:alternative:MRPI:set}
-	X^\infty = \Bigl\{x\in\X: \\
+	X^\infty = \Bigl\{x_0\in\X: \\
 \begin{aligned} 
-&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i} \\
-&x_k\in\X \\ 
+%&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i} w_{k-i} \\
+&x_{k+1} = (A+BK)^{k+1} x_0 + \sum_{i=0}^{k} (A+BK)^{k-i} w_{i} \\
+&x_{k+1}\in\X \\ 
 &Kx_k\in\U \\
@@
 % \begin{equation}
-% 	\X^\infty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
+% 	\Xinfty = \left\{x\in\X: \begin{aligned}&x_k = (A+BK)^k x + \sum_{i=1}^{k} (A+BK)^{k-i-1} w_{k-i}\\
 % 	&x_k\in\X\\
@@
 %
-Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\X^\infty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
-Furthermore, by maximising the volume of $X^\infty$, we can improve the approximation of $\X^\infty$.
+Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\Xinfty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
+Furthermore, by maximising the volume of $X^\infty$, we can improve the approximation of $\Xinfty$.
 
@@
 
-An optimisation program to approximate the positively invariant set $\X^\infty$ can therefore be formulated as
+An optimisation problem whose solution approximates the maximal guaranteed positively invariant set $\Xinfty$ can therefore be formulated as
 %
 \begin{subequations}\label{seq:optimisation:MRPI:abstract}
-	\begin{equation}
-		\max_{\V^\prime} \vol(X^\infty)
-	\end{equation}
+\begin{align}
+		& \max_{\V^\prime} \vol(X^\infty) \\
+%\end{align}
 %
-	subject to
+\intertext{subject to}
 %
-\begin{equation}
-	\V^\prime\subseteq\V
-\end{equation}
-%
-\begin{equation}
-	\vol(\V^\prime)\geq p\cdot\vol(\V)
-\end{equation}
+%\begin{align}
+	& \V^\prime\subseteq\V \\
+% \end{equation}
+% %
+% \begin{equation}
+	& \vol(\V^\prime)\geq p\cdot\vol(\V)
+\end{align}
 \end{subequations}
 %
-In section~\ref{sec:volume:of:hypercube} we discuss how this optimisation can be solved using parallelotopes for~$\V^\prime$.
+In section~\ref{sec:volume:of:hypercube} we discuss how this optimisation can be solved using a parallelotope parameterisation of~$\V^\prime$.
 
-\subsection{Approximating the $n$-step controllable set}\label{ssec:approximating:n:step}
+\section{Approximating the guaranteed $n$-step controllable set}\label{ssec:approximating:n:step}
 %
@@
 %
-That is the set of initial conditions $x_0\in\C_n$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
-$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
+This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences
+$w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
+%$x_k\in\X$, $u_k\in\U$
+(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
 %
-This set is given by
+Thus $\C_n(\T)$ can be expressed as follows.
 %
@@
 \begin{aligned}
-&x_k = A^k x_0 + \sum_{i=1}^{k} A^{k-i}B u_{k-i}(x_{k-i}) + \sum_{i=1}^{k} A^{k-i} w_{k-i}\\
+&x_{k+1} = A^{k+1} x_0 + \sum_{i=0}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=0}^{k} A^{k-i} w_{i}\\
 &x_n\in\T\\
-&x_k\in\X\\
+&x_{k+1}\in\X\\
 &u_k(x_k)\in\U\\
@@
 \end{aligned}\\
-\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n\} \Bigr\}	
+\forall w_k\in\W,\, \forall k\in\{ 0, \ldots , n-1\} \Bigr\}	
 \end{multline*}
@@
 %
-Again, it is easy to verify that the set
+Using Proposition~\ref{prop1} it is easy to verify that the set $C_n(\T)$ defined by
 %
 \begin{multline*}
-C_n(\T) = \Bigl\{ x\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
+C_n(\T) = \Bigl\{ x_0\in\X: \exists \bigl\{u_0(\cdot),\ldots,u_{n-1}(\cdot)\bigr\}\\
 \begin{aligned}
-&x_k = A^k x_0 + \sum_{i=1}^{k} A^{k-i}B u_{k-i}(x_{k-i}) + \sum_{i=1}^{k} A^{k-i} w_{k-i}\\
+&x_{k+1} = A^{k+1} x_0 + \sum_{i=1}^{k} A^{k-i}B u_{i}(x_{i}) + \sum_{i=1}^{k} A^{k-i} w_{i}\\
 &x_N\in\T\\
-&x_k\in\X\\
+&x_{k+1}\in\X\\
 &u_k(x_k)\in\U \\
@@
 \end{aligned}\\
-\forall w_j\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n\} \Bigr\}	
+\forall w_k\in\W,\, \forall v_k\in \V^\prime,\, \forall k\in\{0,\dots,n-1\} \Bigr\}	
 \end{multline*}
@@
 %
-is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with measure $\PP\{\V^\prime\} \geq p$.
+is necessarily contained in $\C_n(\T)$ for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
 %
-As in the case of the positively invariant set, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$.
+As in the case of positively invariant sets, fixing $\V^\prime$ to be a polytopic set leads to a computationally tractable optimisation for the maximisation of~$C_n$.
 This suggests an algorithm for constructing $C_n$ as a polytopic approximation of~$\C_n$ by optimising~$\V^\prime$ so as to maximise the volume of~$C_n$.
@@
 
-In particular the one-step controllable set $C_1(\T)$ for 
+In particular, the one-step controllable set $C_1(\T)$ for the target set 
 \[
@@
 is given by the projection of
+$L_1(\T)\subset \RR^{d+q_{\U}}$, 
+%$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
+defined by
 %
@@
 \end{aligned}\\
-\forall v\in\V^\prime,\, \forall w\in\W\Bigr\}
+\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} ,
 %\end{aligned}
@@
 %
-onto $\RR^d$.
+onto the $x$-subspace.
 %
+Thus
+\[
+C_1(\T) = \{ x : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
+\]
 As all involved sets are polytopic, $L_1(\T)$ is polytopic and its exact projection can be determined computationally.
 
-The optimisation approximating the $n$-step controllable set $\C_n(\T)$ is then given as
+A set $C_n(\T)$ approximating the $n$-step controllable set $\C_n(\T)$ is then given by the solution of the optimisation:
 %
 \begin{subequations}\label{seq:optimisation:n:step:set:abstract}
-	\begin{equation}
-		\max_{\V^\prime} \vol(C_n(\T))
-	\end{equation}
-	subject to
-	\begin{equation}
-	\V^\prime\subseteq\V
-\end{equation}
+\begin{align}
+	& \max_{\V^\prime} \vol(C_n(\T))
+%\end{equation}
+\intertext{subject to}
+%\begin{align}
+	& \V^\prime\subseteq\V  \\
+% \end{equation}
+% %
+% \begin{equation}
+	& \vol(\V^\prime)\geq p\cdot\vol(\V)
+\end{align}
+\end{subequations}
+The property $C_n(\T)\subseteq \C_n(\T)$ then guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.
+
+Note that an additional improvement to the $n$-step controllable set $C_n(\T)$ could be obtained by introducing $\V_1^\prime,\dots,\V_{n-1}^\prime$, to allow different sets $\V_i^\prime$ at each stage.
+% introducing $(n-1)\times 2d$ additional decision variables.
+
+\section{Model Predictive Control}\label{ssec:mpc}
+
+The method proposed for computing $n$-step controllable sets in section~\ref{ssec:approximating:n:step} can be used to formulate a chance constrained Model Predictive Control law.
+In order to minimise conservatism while guaranteeing constraint satisfaction, a closed loop MPC scheme should be used \citep[see e.g.][]{Lee:1997}.
+This involves computing (offline) the set $X^\infty$ using \mbox{(\ref{seq:optimisation:MRPI:abstract}a-c)}, and the 
+sets $C_{i}(X^\infty) = C_1\bigl(C_{i-1}(X^\infty)\bigr)$ and $L_{i}(X^\infty) = L_1\bigl(C_{i-1}(X^\infty)\bigr)$ 
+for $i=1,\ldots,n$ by repeated application of (\ref{seq:optimisation:n:step:set:abstract}a-c) with $C_0(X^\infty)= X^\infty$.
+Online, at each time step $k=0,1,\ldots$, a min-max MPC law is defined by 
+\[
+u_k = u^{(n)}(x_k)
+\]
+where $u^{(n)}(x_k)$ is the solution of
 %
-\begin{equation}
-	\vol(\V^\prime)\geq p\cdot\vol(\V)
-\end{equation}
-\end{subequations}
+\[%\begin{equation}
+\begin{aligned}
+\Bigl( u^{(n)} (x_k) , w^{(n)} (x_k,u) \Bigr) &= \arg \min_{u} \Bigl\{ \max_{w\in\W} J^{(n)}(x_k,u,w)  
+\\
+&\ \quad \text{subject to}\ (x_k, u) \in L_n(\T)
+\Bigr\}
+\end{aligned}
+\]%\end{equation}
+and $J^{(n)}$ is defined by the recursion, for $i=1,\ldots,n$:
+\begin{align*}
+&J^{(i)}(x,u,w) = \tfrac{1}{2}\bigl( \| x \|^2_Q + \| u \|^2_R -
+\gamma^2 \| w \|^2\bigr) + J^{(i-1)}(x^+) 
+\\
+&J^{(i-1)}(x) = J^{(i-1)}\bigl(x,u^{(i-1)}(x),w^{(i-1)}(x,u^{(i-1)}(x))\bigr) \\
+&x^+ = Ax + Bu + Dw
+\end{align*}
+with terminal cost $J^{(0)} = \frac{1}{2}\|x\|_{P_0}^2$.
+%for some suitable terminal weighting matrix $P_0$.
 
-\begin{rem}
-The goal of reformulating a chance constrained model predictive control setup using the proposed method would be to minimise the introduced conservatism.
+An algorithm for solving the online optimization of this min-max robust MPC law is given in~\citet{Buerger2016}. 
 %
-To achieve the best possible performance while guaranteeing constraint satisfaction a closed loop min-max model predictive control problem should be formulated, see e.g.~\cite{Lee:1997}.
-%
-This means that at each stage the decision variables are constrained to be such that the successor state is guaranteed to lie on a feasible trajectory to the target set.
-%
-Therefore to reformulate a chance constrained model predictive control problem as a deterministically constrained problem with guaranteed probabilistic feasibility and guaranteed recursive feasibility, the sets $C_n(\T)$ can be introduced as stage constraints, and the target set $\T$ can be chosen as the robust positively invariant set $X^\infty$.
-\end{rem}
+Since the stage constraints are constructed using the controllable sets $C_{i}(X^\infty)$, the decision variables are constrained at each stage to be such that the successor state is guaranteed to lie on a feasible trajectory to the target set $X^\infty$.
+Therefore the MPC law solves a deterministically constrained problem with guaranteed probabilistic feasibility and guaranteed recursive feasibility.
 
-\section{The Volume of a Transformed Hypercube}\label{sec:volume:of:hypercube}
+% \begin{rem}
+% The goal of reformulating a chance constrained model predictive control setup using the proposed method would be to minimise the introduced conservatism.
+% %
+% To achieve the best possible performance while guaranteeing constraint satisfaction a closed loop min-max model predictive control problem should be formulated \cite[see e.g.][]{Lee:1997}.
+% %
+% This means that at each stage the decision variables are constrained to be such that the successor state is guaranteed to lie on a feasible trajectory to the target set.
+% %
+% Therefore to reformulate a chance constrained model predictive control problem as a deterministically constrained problem with guaranteed probabilistic feasibility and guaranteed recursive feasibility, the sets $C_n(\T)$ can be introduced as stage constraints, and the target set $\T$ can be chosen as the robust positively invariant set $X^\infty$.
+% \end{rem}
+
+%\section{The Volume of a Transformed Hypercube}\label{sec:volume:of:hypercube}
+
+\section{Parameterisation using  parallelotopes}\label{sec:volume:of:hypercube}
 %
 %
-In this section we present a method that enables optimisation over polytopes, as is required to solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract}.
+In this section we present a method that enables optimisation over polytopes, as is required to solve~(\ref{seq:optimisation:MRPI:abstract}a-c) and~(\ref{seq:optimisation:n:step:set:abstract}a-c).
 %
@@
 %
-It is known that the volume of an object is translation invariant, i.e. 
+%It is known that the volume of an object is translation invariant, i.e. 
+and since the volume of an object is translation invariant we have 
 \begin{multline*}
@@
 \end{multline*}
-By using $v_0$ and $t_i$ as decision variables we can solve~\eqref{seq:optimisation:MRPI:abstract} and~\eqref{seq:optimisation:n:step:set:abstract} by solving an optimisation program with $2d$ decision variables.
+Using $v_0$ and $t_i$ as decision variables we can solve~(\ref{seq:optimisation:MRPI:abstract}a-c) and~(\ref{seq:optimisation:n:step:set:abstract}a-c) by solving an optimisation program with $2d$ decision variables.
 %
@@
 
-The problem formulation~\eqref{seq:optimisation:MRPI:abstract} can therefore be reformulated as
+The optimisation~(\ref{seq:optimisation:MRPI:abstract}a-c) can therefore be reformulated as
 %
@@
 
-Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
 %
@@
 %
-The uniqueness of a maximiser for the volume of a set however is less transparent and can in general not be guaranteed.
+However, the uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent and cannot be guaranteed in general.
 
@@
 %
-In this section we present a two dimensional example for each proposed scheme.
+In this section we use a two dimensional example to illustrate the computation of guaranteed invariant and guaranteed $n$-step controllable sets.
 %
-First we illustrate the approximation of the guaranteed positively invariant set~$X^\infty$ for the system
+First we illustrate the approximation of the maximal guaranteed positively invariant set~$\X^\infty$ for the system
 %
@@
 subject to the constraints 
-\begin{align*}
-\X &= \{x:\norm{x}_\infty\leq15\}, \\
-\U &= \{u:\abs{u}\leq2\}, \\
-\W &= \{w:\norm{w}_1\leq1\}.
-\end{align*}
+\begin{equation}\label{eq:example:rconstriaints}
+\begin{aligned}
+\X &= \{x\in\RR^2 :\norm{x}_\infty\leq15\}, \\
+\U &= \{u\in\RR :\abs{u}\leq2\}, \\
+\W &= \{w\in\RR^2 :\norm{w}_1\leq1\}.
+\end{aligned}
+\end{equation}
 %
@@
 %
-\begin{equation}
+\[%\begin{equation}
 	y = \begin{pmatrix}-0.08&-0.05\\
@@
 0.44\\0.44\end{pmatrix}u + v
-\end{equation}
+\]%\end{equation}
 %
@@
 %
-\begin{equation}
+\begin{equation}\label{eq:example:pconstriaint}
 	\PP\{\norm{y}_\infty\leq 1\}\geq 0.3
@@
 \[
-v_1 = \begin{pmatrix} 0.07 \\ 0.08\end{pmatrix} \quad \text{and}\quad 
-v_2 = \begin{pmatrix}-0.07 \\ 0.08\end{pmatrix},
+v_1 = \begin{pmatrix} 0.08 \\ 0.07\end{pmatrix} \quad \text{and}\quad 
+v_2 = \begin{pmatrix}-0.08 \\ 0.07\end{pmatrix},
 \] 
@@
 %
-Although we can not make statements on convexity of the volume in this parametrisation the optimisation converges to the same maximiser for different initialisers, furthermore numeric evaluation of the Hessian at the maximiser reveals that one eigenvalue vanishes.
+Although we are unable to make a statement on convexity of the volume $\vol(X^\infty)$ in this parametrisation, the optimisation converges to the same maximiser for different initialisers.
+Numerical evaluation of the Hessian reveals that this is indeed a (local) maximum point, although one eigenvalue vanishes at the solution.
+%, furthermore numerical evaluation of the Hessian at the maximiser reveals that one eigenvalue vanishes. 
 %
 
-In order to compare the proposed method with existing results we compute a sample based set as described in~\cite{Zhang2015}, that is we compute the smallest set containing enough samples guarantee constraint satisfaction with a confidence of $1-\beta$.
+In order to compare the proposed method with existing results we compute a sample-based set as described in~\cite{Zhang2015}, that is we compute the smallest set $\V^\prime$ containing enough samples to guarantee constraint satisfaction with a confidence of $1-\beta$.
 %
-To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation is given as
+To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation~\citep[eq.~(10)]{Zhang2015} is given as
 %
@@
 \begin{equation}
-\Gamma_i \bfa{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\dots,4\}
+\Gamma_i \hat{v}^{(j)}\leq \gamma_i ,\ i\in\{1,\ldots,4\}, \ j = 1,\ldots,N
 \end{equation}
@@
 %
-Where $\bfa{v}^{(j)}$ are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=1e-3$, the number of samples necessary to satisfy this requirement is given by cumulative binomial distribution but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for our choice $N = 4714$.
+Where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$ and
+%$\hat{v}^{(j)}$, $j=1,\ldots,N$ 
+$\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
+are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$.
+The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for this example $N = 4714$.
 %
@@
 \includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
-\caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
+\caption{The guaranteed positively invariant set $X^\infty$ computed using~(\ref{seq:optimisation:MRPI:abstract}a-c) 
+%of the system~\eqref{eq:example:system:MRPI} 
+in red, and in blue the robust positively invariant set for the disturbance set computed using the methods discussed in~\cite{Zhang2015} with 
+%a confidence level of $0.999$.}
+confidence $1-\beta$, $\beta = 0.001$.}
 \label{fig:MRPI:optimised}
@@
 
-For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$.
+For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
 %
-Again the result illustrated in figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
+%
+Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
 %
@@
 \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue).
-The additional sets are remaining $C_1(\T),C_2(\T)$ and $C_3(\T)$ for the comparison set obtained with~\eqref{eq:comparison:set} and the optimised~$\V^\prime$ obtained with the proposed method.}
+Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.
+For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with
+confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
 \label{fig:n:step:controllable:set}
@@
 
-\section{Conclusion}\label{sec:conclusion}
+\section{Conclusions and future work}\label{sec:conclusion}
 %
 %
-In this paper we presented a method in which the positively invariant set and the $n$-step controllable set of a stochastically constrained system are approximated respectively.
+In this paper we present methods for approximating the positively invariant set and the $n$-step controllable set of a chance constrained stochastic system.
 %
-The method we present is based on a simple restriction of the set $\V^\prime\subseteq$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
+The approach we present is based on a simple restriction of the set $\V^\prime$ to be a parallelotope; this yields remarkable results in simulations and avoids the introduction of non-convex constraints in the optimisation problems (\ref{seq:optimisation:MRPI:abstract}a-c) and \mbox{(\ref{seq:optimisation:n:step:set:abstract}a-c)}.
  %
-Although the presented scheme scales well to higher dimensions, the complexity of positively invariant sets and $n$-step controllable sets does not.
+
+Although the presented scheme scales well to higher dimensions, the complexity of positively invariant sets and $n$-step controllable sets does not in general, and this could lead to computational intractability in the objective functions (\ref{seq:optimisation:MRPI:abstract}a) and (\ref{seq:optimisation:n:step:set:abstract}a) when the state dimension $d$ is large.
 %
-The underlying probability distribution was assumed to be uniform for ease of presentation, a similar method may be applied as long as the probability measure of a parallelotope can be analytically determined.
+
+The underlying probability distribution was assumed to be uniform for ease of presentation, a similar method may be applied to more general distributions as long as they allow the probability measure of a parallelotope to be analytically determined.
 %
-An additional improvement to the $n$-step controllable set $C_n(\T)$ could be obtained by introducing $\V_1^\prime,\dots,\V_{n-1}^\prime$, to allow different sets $\V_i^\prime$ at each stage introducing $(n-1)\times 2d$ additional decision variables.
+Future work will remove this restriction by approximating non-uniform probability distributions as discrete distributions defined by collections of spatially distributed point masses.
+%
+This would necessarily introduce a degree of uncertainty in the probability measure of $\V^\prime$.
+However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by sample based approaches), which would allow for guarantees of constraint satisfaction.
 

### 2016-11-07 draft.tex
Added figure + minor changes.
what happened

[ticket: X]

--- 2016-11-05 draft.tex
@@
 %
-That is the set of initial conditions $x_0\in\C_n$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
+That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
 $w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
@@
 
-In particular the one-step controllable set $C_1(\T)$ for 
-\[
-\T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
-\]
+In particular the one-step controllable set $C_1(\T)$ for a polytopic~$\T$
+% \[
+% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
+% \]
 is given by the projection of 
@@
 
-Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for a constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
 %
@@
 %
-The resulting sets are illustrated in Figure~\ref{fig:MRPI:optimised}.
+The resulting sets are illustrated in Figure~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}.
 %
+\begin{figure}
+\includegraphics[width=.95\linewidth]{Vprime.pdf}
+\caption{The set~$\V^\prime$ resulting the optimisation~\eqref{seq:optimisation:MRPI:precise} for the discussed requirements in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow} with $\PP\{v\in\V^\prime\}=0.3$, and in \textcolor{red}{red}, the set satisfying~\eqref{eq:comparison:set}, with the defining samples.
+The comparison set contains $99.91$\% of the total volume of $\V$.}
+\label{figure:V:prime:and:comparison}
+\vspace{4mm}
+\end{figure}
 
@@
 \includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
-\caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in red, blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
+\caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
 \label{fig:MRPI:optimised}
@@
 
-For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$.
+For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
 %
-Again the result illustrated in figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
 %
@@
 \includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
-\caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue).
-The additional sets are remaining $C_1(\T),C_2(\T)$ and $C_3(\T)$ for the comparison set obtained with~\eqref{eq:comparison:set} and the optimised~$\V^\prime$ obtained with the proposed method.}
+\caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue).
+The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
 \label{fig:n:step:controllable:set}
@@
 %
-The method we present is based on a simple restriction of the set $\V^\prime\subseteq$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
+The method we present is based on a simple restriction of the set $\V^\prime\subseteq\V$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
 %

### 2016-11-07 draft.tex

--- 2016-11-06 draft.tex
@@
 %
+That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
+$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
+%
 This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences
@@
 
-In particular, the one-step controllable set $C_1(\T)$ for the target set 
-\[
-\T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
-\]
+In particular the one-step controllable set $C_1(\T)$ for a polytopic~$\T$
+% \[
+% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
+% \]
+is given by the projection of 
+%
+In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
+% \[
+% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
+% \]
 is given by the projection of
@@
 %
-
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for a constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+%
 Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
@@
 \includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
+% \caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
 \caption{The guaranteed positively invariant set $X^\infty$ computed using~(\ref{seq:optimisation:MRPI:abstract}a-c) 
@@
 
+For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
+%
+Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+%
 For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
@@
 \includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
+% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue).
+The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
 \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue).
@@
 In this paper we present methods for approximating the positively invariant set and the $n$-step controllable set of a chance constrained stochastic system.
+%
+The method we present is based on a simple restriction of the set $\V^\prime\subseteq\V$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
 %

### 2016-11-07 draft.tex
Found typo.
what happened

[ticket: X]
final (?) edits to draft

--- 2016-11-06 draft.tex
@@
 \begin{keyword}                           % Five to ten keywords,  
-Keyword 1; keyword 2;
+Robust control; chance constraints; stochastic MPC; positively invariant sets.
 \end{keyword}                             % keyword list or with the 
@@
 \begin{abstract}                          % Abstract of not more than 250 words.
-This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to chance constraints.
+This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to ch````ance constraints.
 The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints of the control problem.
@@
 %
-The properties of such sets and the algorithms to compute them are well known and documented in the literature.
+The properties of such sets and the algorithms to compute them are well known and are documented in the literature.
 %
@@
 %
-By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the probabilistically constrained system.
+By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the chance constrained system.
 
@@
 %
-This paper is organised  as follows:
+The paper is organised  as follows:
 In section~\ref{sec:setup} we present the problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, conditions that define the positively invariant set under chance constraints.
@@
 %
-The parametrisation of a parallelotope is discussed in~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
+A parametrisation employing parallelotopes is discussed in section~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
 %
-Two numerical examples are presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the presentation and sketch possible extensions to the presented scheme.
+A numerical example is presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the paper and sketch possible extensions to the proposed scheme.
 
@@
 Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\Xinfty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
-Furthermore, by maximising the volume of $X^\infty$, we can improve the approximation of $\Xinfty$.
+Furthermore, by maximising the volume of $X^\infty$ we can improve the approximation of $\Xinfty$.
 
@@
 %with $X_0= \X$.
-Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ once $X_k\subseteq X_{k+1}$.
+Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ if $X_k\subseteq X_{k+1}$.
 
@@
 %
-This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences
+%That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
+%$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
+%
+This is defined as the set of initial states $x_0$ of (\ref{eq:system}) such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences
 $w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
@@
 
-In particular, the one-step controllable set $C_1(\T)$ for the target set 
-\[
-\T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
-\]
-is given by the projection of
-$L_1(\T)\subset \RR^{d+q_{\U}}$, 
+In particular, the one-step controllable set $C_1(\T)$ for a polytopic
+target set~$\T$
+% \[
+% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
+% \]
+% is given by the projection of 
+%
+%In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
+% \[
+% \T = \Bigl\{x\in\RR^d : J_i x\leq1,\ i\leq M_\T\Bigr\}
+% \]
+is given by the projection on to the $x$-subspace of the polytopic set $L_1(\T)\subset \RR^{d+q_{\U}}$, 
 %$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
@@
 \end{aligned}\\
-\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} ,
+\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} .
 %\end{aligned}
@@
 %
-onto the $x$-subspace.
+%onto the $x$-subspace.
 %
@@
 \end{subequations}
-The property $C_n(\T)\subseteq \C_n(\T)$ then guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.
+The property $C_n(\T)\subseteq \C_n(\T)$ guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.
 
@@
 In order to minimise conservatism while guaranteeing constraint satisfaction, a closed loop MPC scheme should be used \citep[see e.g.][]{Lee:1997}.
-This involves computing (offline) the set $X^\infty$ using \mbox{(\ref{seq:optimisation:MRPI:abstract}a-c)}, and the 
+This involves computing (offline) the set $X^\infty$ using \mbox{(\ref{seq:optimisation:MRPI:abstract}a-c)}, and (also offline) the 
 sets $C_{i}(X^\infty) = C_1\bigl(C_{i-1}(X^\infty)\bigr)$ and $L_{i}(X^\infty) = L_1\bigl(C_{i-1}(X^\infty)\bigr)$ 
@@
 \\
-&\ \quad \text{subject to}\ (x_k, u) \in L_n(\T)
+&\ \quad \text{subject to}\ (x_k, u) \in L_n(X^\infty)
 \Bigr\}
@@
 %
-Recall that 
+Recall also that 
 \[
@@
 %
-
-Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore the constraint $\prod_i t_i \geq c$, for a constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+%
+%Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
 %
@@
 %
-However, the uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent and cannot be guaranteed in general.
+The uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent however, and cannot be guaranteed in general.
 
@@
 %
-Although we are unable to make a statement on convexity of the volume $\vol(X^\infty)$ in this parametrisation, the optimisation converges to the same maximiser for different initialisers.
+Although we are unable to make a statement on convexity of the volume $\vol(X^\infty)$ in this parametrisation, the optimisation converges to the same maximiser (shown in Figure~\ref {figure:V:prime:and:comparison}) for different initialisers.
 Numerical evaluation of the Hessian reveals that this is indeed a (local) maximum point, although one eigenvalue vanishes at the solution.
@@
 %
-To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation~\citep[eq.~(10)]{Zhang2015} is given as
+To obtain a comparable result we use again constrain $\V^\prime $ to be a scaled version of $\V$, so that $\V^\prime = \{v : \Gamma_i v \leq \gamma_i, \, i =1,\ldots,4\}$, where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$.
+%
+The optimisation~\citep[eq.~(10)]{Zhang2015} is then given as
 %
@@
 %
-Where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$ and
 %$\hat{v}^{(j)}$, $j=1,\ldots,N$ 
-$\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
+where $\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
 are the samples used to satisfy the probabilistic requirements with the  given confidence of $\beta=0.001$.
@@
 %
-The resulting sets are illustrated in Figure~\ref{fig:MRPI:optimised}.
+
+The resulting sets $\V^\prime$ and $X^\infty$ are shown in Figures~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}. 
 %
+The set $\V^\prime$ computed using (\ref{eq:comparison:set}a,b) is clearly suboptimal (Fig.~\ref{figure:V:prime:and:comparison}), and in fact it contains $99.91$\% of the total volume of $\V$. 
+This suboptimality is a result of the requirement for a high level of confidence ($1-\beta = 0.999$), and is reflected in a reduction in volume of the associated positively invariant set (Fig.~\ref{fig:MRPI:optimised}).
 
+%
 \begin{figure}
-\includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
-\caption{The guaranteed positively invariant set $X^\infty$ computed using~(\ref{seq:optimisation:MRPI:abstract}a-c) 
+\includegraphics[width=0.99\linewidth]{Vprime.pdf}
+\caption{The set~$\V^\prime$ resulting from the
+  optimisation \mbox{(\ref{seq:optimisation:MRPI:precise}a-d)}
+with
+  $\PP\{v\in\V^\prime\}=0.3$
+in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow}. In \textcolor{red}{red}, the set $\V^\prime$
+  computed using~(\ref{eq:comparison:set}a-b) for a confidence level of $1-\beta=0.999$. The 
+  samples $\{\hat{v}^{(j)},\ldots,\hat{v}^{(N)}\}$ are shown in \textcolor{blue}{blue}.}
+\label{figure:V:prime:and:comparison}
+\vspace{2mm}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.99\linewidth]{MRPIsetOptimised.pdf}
+% \caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
+\caption{The guaranteed positively invariant set $X^\infty$ computed using
+\mbox{(\ref{seq:optimisation:MRPI:precise}a-d)}
+%(\ref{seq:optimisation:MRPI:abstract}a-c) 
 %of the system~\eqref{eq:example:system:MRPI} 
-in red, and in blue the robust positively invariant set for the disturbance set computed using the methods discussed in~\cite{Zhang2015} with 
-%a confidence level of $0.999$.}
-confidence $1-\beta$, $\beta = 0.001$.}
+in \textcolor{red}{red}, and in \textcolor{blue}{blue} the robust positively invariant set for the disturbance set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b)
+with a confidence level of $1-\beta = 0.999$.}
 \label{fig:MRPI:optimised}
-\vspace{4mm}\end{figure}
+\vspace{2mm}\end{figure}
 
-For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
+% For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
+% %
+% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
 %
-by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
+For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, with $\T=X^\infty$,
 %
-Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+by solving (\ref{seq:optimisation:n:step:precise}a-d) for $C_1(X^\infty)$, $C_2(X^\infty)$, $C_3(X^\infty)$, where $X^\infty$ is the guaranteed positively invariant set computed via (\ref{seq:optimisation:MRPI:precise}a-d).
 %
+Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} are reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace.
+The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b).
+Clearly the high level of suboptimality in this choice of $\V^\prime$,
+which is a consequence of 
+%that results from 
+the requirement for a high level of confidence of satisfaction of the chance constraint, translates to suboptimality in the computed sets $C_n(X^\infty)$.
+%
+% For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
+% %
+% by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
+% %
+% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+% %
 
-\begin{figure}
-\includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
-\caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue).
+\begin{figure}[ht]
+\includegraphics[width=.99\linewidth]{NStepSetOptimised.pdf}
+% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue).
+The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
+\caption{Approximation of the guaranteed 3-step controllable set for a $\T=X^\infty$ (in \textcolor{blue}{blue}).
 Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.
-For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with
-confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
+For comparison, the controllable sets obtained for a fixed $\V^\prime$ computed using~(\ref{eq:comparison:set}a,b) with
+confidence $1-\beta= 0.999$ are shown in dashed lines.}
 \label{fig:n:step:controllable:set}
@@
 In this paper we present methods for approximating the positively invariant set and the $n$-step controllable set of a chance constrained stochastic system.
+%
+%The method we present is based on a simple restriction of the set $\V^\prime$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
 %
@@
 %
-Future work will remove this restriction by approximating non-uniform probability distributions as discrete distributions defined by collections of spatially distributed point masses.
+Future work will remove this restriction by approximating non-uniform probability densities as discrete distributions defined by collections of spatially distributed point masses.
 %
 This would necessarily introduce a degree of uncertainty in the probability measure of $\V^\prime$.
-However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by sample based approaches), which would allow for guarantees of constraint satisfaction.
+However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by a sample based approach), which would allow for a deterministic guarantee of constraint satisfaction.
 

### 2016-11-07 draft.tex
corrected a typo in the abstract

@@
 \begin{abstract}                          % Abstract of not more than 250 words.
-This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to ch````ance constraints.
+This paper proposes a method of approximating positively invariant sets and $n$-step controllable sets of uncertain linear systems that are subject to chance constraints.
 The computed sets are robustly invariant and are guaranteed to satisfy the probabilistic constraints of the control problem.

### 2016-11-08 draft.tex
version submitted 8 Nov

@@
 
-\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
+\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}%\thanksref{footnoteinfo}} 
 % Title, preferably not more than 10 words.
@@
 \begin{keyword}                           % Five to ten keywords,  
-Robust control; chance constraints; stochastic MPC; positively invariant sets.
+Robust control; chance constraints;  invariant sets; stochastic MPC.
 \end{keyword}                             % keyword list or with the 
@@
 \begin{aligned}
-  & X_0 = \X \\
+  & X_0 = \X\cap K^{-1}\mathcal U \\
   & \begin{aligned}
@@
 \begin{thm}\label{thm2}
-Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in\X$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that
+Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in X_0$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that
 yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
 \end{thm}
+%
+The matrix~$\Gamma$ is an analytical object and can be made up of~$E_i$ and~$F_iK$, but does not need to contain all inequalities supporting~$X_0$, e.g. in asymmetrical cases.
+%
+\\[1em]
 %
@@
 X_{d-1} 
-&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k}\X\\
+&\subseteq\bigcap_{k\leq d-1}(A+BK)^{-k} X_0\\
 &\subseteq \Bigl\{x:\pm\Gamma x\leq\bfa{1}\wedge\dots\wedge\pm\Gamma(A+BK)^{d-1} x\leq\bfa{1} \Bigr\}\\
@@
 \]
-holds, where $\rho$ denotes the spectral radius of $A+BK$.
+holds, where $\rho$ denotes the spectral radius of $A+BK$, such a matrix can be found using semi-definite programming.
 %
@@
 \[
-C_1(\T) = \{ x : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
+C_1(\T) = \{ x\in\mathcal X : \exists u \ \text{such that} \ (x,u)\in L_1(\T)\}.
 \]
@@
 %$\hat{v}^{(j)}$, $j=1,\ldots,N$
-where $\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
-are the samples used to satisfy the probabilistic requirements with the  given confidence of $\beta=0.001$.
-The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{\beta}(2-\log(p))$, so for this example $N = 4714$.
+
+where $\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$ are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$. 
+%
+The number of samples that are needed to satisfy this requirement is given by the cumulative binomial distribution, but can be overestimated to be $N \geq \frac{2}{1-p}(2-\log(\beta))$, so for this example $N = 26$.
 %
@@
 The resulting sets $\V^\prime$ and $X^\infty$ are shown in Figures~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}.
+
 %
-The set $\V^\prime$ computed using (\ref{eq:comparison:set}a,b) is clearly suboptimal (Fig.~\ref{figure:V:prime:and:comparison}), and in fact it contains $99.91$\% of the total volume of $\V$. 
-This suboptimality is a result of the requirement for a high level of confidence ($1-\beta = 0.999$), and is reflected in a reduction in volume of the associated positively invariant set (Fig.~\ref{fig:MRPI:optimised}).
+The set $\V^\prime$ computed using (\ref{eq:comparison:set}a,b) is clearly sub-optimal (Fig.~\ref{figure:V:prime:and:comparison}), and in fact it contains $80.77$\% of the total volume of $\V$.
+%
+This sub-optimality is a result of the requirement for a high level of confidence ($1-\beta = 0.999$), and is reflected in a reduction in volume of the associated positively invariant set (Fig.~\ref{fig:MRPI:optimised}).
 
@@
 \begin{figure}
+% \includegraphics[width=.95\linewidth]{Vprime.pdf}
+% \caption{The set~$\V^\prime$ resulting the optimisation~\eqref{seq:optimisation:MRPI:precise} for the discussed requirements in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow} with $\PP\{v\in\V^\prime\}=0.3$, and in \textcolor{red}{red}, the set satisfying~\eqref{eq:comparison:set}, with the defining samples.
+The comparison set contains $80.77$\% of the total volume of $\V$.}
 \includegraphics[width=0.99\linewidth]{Vprime.pdf}
-\caption{The set~$\V^\prime$ resulting from the
-  optimisation \mbox{(\ref{seq:optimisation:MRPI:precise}a-d)}
-with
-  $\PP\{v\in\V^\prime\}=0.3$
-in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow}. In \textcolor{red}{red}, the set $\V^\prime$
-  computed using~(\ref{eq:comparison:set}a-b) for a confidence level of $1-\beta=0.999$. The 
-  samples $\{\hat{v}^{(j)},\ldots,\hat{v}^{(N)}\}$ are shown in \textcolor{blue}{blue}.}
+\caption{The set~$\V^\prime$ resulting from the optimisation \mbox{(\ref{seq:optimisation:MRPI:precise}a-d)} with $\PP\{v\in\V^\prime\}=0.3$ in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow}. 
+%
+In \textcolor{red}{red}, the set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b) for a confidence level of $1-\beta=0.999$. 
+%
+The samples $\{\hat{v}^{(1)},\ldots,\hat{v}^{(26)}\}$ are shown in \textcolor{blue}{blue}.}
 \label{figure:V:prime:and:comparison}
-\vspace{2mm}
+% \vspace{2mm}
 \end{figure}
@@
 \includegraphics[width=.99\linewidth]{MRPIsetOptimised.pdf}
-% \caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
-\caption{The guaranteed positively invariant set $X^\infty$ computed using
-\mbox{(\ref{seq:optimisation:MRPI:precise}a-d)}
-%(\ref{seq:optimisation:MRPI:abstract}a-c) 
-%of the system~\eqref{eq:example:system:MRPI} 
-in \textcolor{red}{red}, and in \textcolor{blue}{blue} the robust positively invariant set for the disturbance set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b)
-with a confidence level of $1-\beta = 0.999$.}
+\caption{The guaranteed positively invariant set $X^\infty$ computed using~\mbox{(\ref{seq:optimisation:MRPI:precise}a-d)} in \textcolor[rgb]{0,0.5216,0.7373}{blue}, and in \textcolor[rgb]{1,0,0}{dashed red} the robust positively invariant set for the disturbance set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b) with a confidence level of $1-\beta = 0.999$.}
 \label{fig:MRPI:optimised}
@@
 %
-Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} are reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace.
+Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace. 
+%
 The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b).
-Clearly the high level of suboptimality in this choice of $\V^\prime$,
-which is a consequence of 
-%that results from 
-the requirement for a high level of confidence of satisfaction of the chance constraint, translates to suboptimality in the computed sets $C_n(X^\infty)$.
+%
+Clearly the high level of sub-optimality in this choice of $\V^\prime$, which is a consequence of the requirement for a high level of confidence of satisfaction of the chance constraint, translates to sub-optimality in the computed sets $C_n(X^\infty)$.
+\textcolor{red}{Did we not say that 5 sentences ago?}
 %
@@
 
+% \begin{figure}
+% \includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
+% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (\textcolor[rgb]{0.4667,0.6745,0.1882}{in green}). 
+% % The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
+% % \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue). 
+% Sets $C_1(X^\infty)$, $C_2(X^\infty)$ and $C_3(X^\infty)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.
+For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with
+% confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
 \begin{figure}[ht]
@@
 The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
-\caption{Approximation of the guaranteed 3-step controllable set for a $\T=X^\infty$ (in \textcolor{blue}{blue}).
+\caption{Approximation of the guaranteed 3-step controllable set for a $\T=X^\infty$ (in \textcolor[rgb]{0.4667,0.6745,0.1882}{green}).
 Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.

### 2017-02-28 draft.tex
Post-acceptance changes.
what happened

[ticket: X]

@@
 
-\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}%\thanksref{footnoteinfo}} 
+\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
 % Title, preferably not more than 10 words.
@@
 \begin{keyword}                           % Five to ten keywords,  
-Robust control; chance constraints;  invariant sets; stochastic MPC.
+Keyword 1; keyword 2;
 \end{keyword}                             % keyword list or with the 
@@
 %
-The properties of such sets and the algorithms to compute them are well known and are documented in the literature.
+The properties of such sets and the algorithms to compute them are well known and documented in the literature.
 %
@@
 %
-By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the chance constrained system.
+By maximising the size of the $n$-step controllable set we indirectly approximate the $n$-step controllable set of the probabilistically constrained system.
 
@@
 %
-The paper is organised  as follows:
+This paper is organised  as follows:
 In section~\ref{sec:setup} we present the problem formulation and derive, in section~\ref{ssec:approximating:MRPI}, conditions that define the positively invariant set under chance constraints.
@@
 %
-A parametrisation employing parallelotopes is discussed in section~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
+The parametrisation of a parallelotope is discussed in~\ref{sec:volume:of:hypercube} and the general problem formulations introduced in section~\ref{sec:setup} are made precise for this parametrisation.
 %
-A numerical example is presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the paper and sketch possible extensions to the proposed scheme.
+Two numerical examples are presented in section~\ref{sec:examples} to illustrate the proposed scheme in two dimensions and in section~\ref{sec:conclusion} we conclude the presentation and sketch possible extensions to the presented scheme.
 
@@
 Then from Proposition~\ref{prop1}, the inclusion $X^\infty\subseteq\Xinfty$ necessarily holds for any $\V^\prime\subseteq\V$ with probability measure $\PP\{\V^\prime\} \geq p$.
-Furthermore, by maximising the volume of $X^\infty$ we can improve the approximation of $\Xinfty$.
+Furthermore, by maximising the volume of $X^\infty$, we can improve the approximation of $\Xinfty$.
 
@@
 %with $X_0= \X$.
-Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ if $X_k\subseteq X_{k+1}$.
+Clearly $X_k = \bigcap_{l=0,\ldots,k}\E_l$ and, analogously to the conventional MRPI calculation~\citep{Kolmanovsky:1998}, the iteration therefore gives $X_k = X^\infty$ once $X_k\subseteq X_{k+1}$.
 
@@
 %
-%That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
-%$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
+That is the set of initial conditions $x_0\in\C_n(\T)$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, $x_n\in\T$, for all admissible disturbance sequences
+$w\in\W$, while guaranteeing that the robust state and input constraints~(\ref{eq:state_input:constraints}) and the probabilistic constraint~(\ref{eq:probabilistic:constraint}) are satisfied.
 %
-This is defined as the set of initial states $x_0$ of (\ref{eq:system}) such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences
+This is defined as the set of initial conditions $x_0\in\X$ such that a sequence of control inputs exists that drives the state in $n$ steps to the target set, so that $x_n\in\T$ for all admissible disturbance sequences
 $w_k\in\W$, $k=0,\ldots,n-1$, while guaranteeing that the robust state and input constraints 
@@
 
-In particular, the one-step controllable set $C_1(\T)$ for a polytopic
-target set~$\T$
+In particular the one-step controllable set $C_1(\T)$ for a polytopic~$\T$
 % \[
@@
 % \]
-% is given by the projection of 
+is given by the projection of 
 %
-%In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
+In particular, the one-step controllable set $C_1(\T)$ for the polytopic target set~$\T$
 % \[
@@
 % \]
-is given by the projection on to the $x$-subspace of the polytopic set $L_1(\T)\subset \RR^{d+q_{\U}}$, 
+is given by the projection of
+$L_1(\T)\subset \RR^{d+q_{\U}}$, 
 %$L_1(\T)\subset \RR^d\times \RR^{q_{\U}}$, 
@@
 \end{aligned}\\
-\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} .
+\forall v\in\V^\prime,\, \forall w\in\W\Bigr\} ,
 %\end{aligned}
@@
 %
-%onto the $x$-subspace.
+onto the $x$-subspace.
 %
@@
 \end{subequations}
-The property $C_n(\T)\subseteq \C_n(\T)$ guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.
+The property $C_n(\T)\subseteq \C_n(\T)$ then guarantees the existence of a control sequence such that the constraints~(\ref{eq:state_input:constraints}) and (\ref{eq:probabilistic:constraint}) are met and $x_n\in\T$ for all $x_0\in C_n(\T)$.
 
@@
 In order to minimise conservatism while guaranteeing constraint satisfaction, a closed loop MPC scheme should be used \citep[see e.g.][]{Lee:1997}.
-This involves computing (offline) the set $X^\infty$ using \mbox{(\ref{seq:optimisation:MRPI:abstract}a-c)}, and (also offline) the 
+This involves computing (offline) the set $X^\infty$ using \mbox{(\ref{seq:optimisation:MRPI:abstract}a-c)}, and the 
 sets $C_{i}(X^\infty) = C_1\bigl(C_{i-1}(X^\infty)\bigr)$ and $L_{i}(X^\infty) = L_1\bigl(C_{i-1}(X^\infty)\bigr)$ 
@@
 %
-Recall also that 
+Recall that 
 \[
@@
 %
-Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore the constraint $\prod_i t_i \geq c$, for a constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for a constant $c$, is convex for $t_i>0$, so that the constraints in~\eqref{seq:optimisation:MRPI:precise} and~\eqref{seq:optimisation:n:step:precise} are convex.
 %
-%Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
+Note that~\eqref{eq:containment:linear:1} and~\eqref{eq:linear:inequalites:on:t:1} are linear constraints on $v_0$ and $t_i$, furthermore recall that $\prod_i t_i \geq c$, for constant $c$, is convex for $t_i>0$, so that the constraints in~(\ref{seq:optimisation:MRPI:precise}a-d) and~(\ref{seq:optimisation:n:step:precise}a-d) are convex.
 %
@@
 %
-The uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent however, and cannot be guaranteed in general.
+However, the uniqueness of a maximiser for the volume in the objective functions (\ref{seq:optimisation:MRPI:precise}a) and (\ref{seq:optimisation:n:step:precise}a) is less transparent and cannot be guaranteed in general.
 
@@
 %
-Although we are unable to make a statement on convexity of the volume $\vol(X^\infty)$ in this parametrisation, the optimisation converges to the same maximiser (shown in Figure~\ref {figure:V:prime:and:comparison}) for different initialisers.
+Although we are unable to make a statement on convexity of the volume $\vol(X^\infty)$ in this parametrisation, the optimisation converges to the same maximiser for different initialisers.
 Numerical evaluation of the Hessian reveals that this is indeed a (local) maximum point, although one eigenvalue vanishes at the solution.
@@
 %
-To obtain a comparable result we use again constrain $\V^\prime $ to be a scaled version of $\V$, so that $\V^\prime = \{v : \Gamma_i v \leq \gamma_i, \, i =1,\ldots,4\}$, where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$.
-%
-The optimisation~\citep[eq.~(10)]{Zhang2015} is then given as
+To obtain a comparable result we use again use a scaled version of $\V$, so that the optimisation~\citep[eq.~(10)]{Zhang2015} is given as
 %
@@
 %
+Where $\V = \{v : \Gamma_i v \leq 1, \, i =1, \ldots ,4\}$ and
 %$\hat{v}^{(j)}$, $j=1,\ldots,N$ 
-
-where $\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$ are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$. 
+$\hat{v}^{(1)},\ldots,\hat{v}^{(N)}$
+are the samples used to satisfy the probabilistic requirements with the given confidence of $\beta=0.001$. 
 %
@@
 %
-
-The resulting sets $\V^\prime$ and $X^\infty$ are shown in Figures~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}.
-
-%
-The set $\V^\prime$ computed using (\ref{eq:comparison:set}a,b) is clearly sub-optimal (Fig.~\ref{figure:V:prime:and:comparison}), and in fact it contains $80.77$\% of the total volume of $\V$.
-%
-This sub-optimality is a result of the requirement for a high level of confidence ($1-\beta = 0.999$), and is reflected in a reduction in volume of the associated positively invariant set (Fig.~\ref{fig:MRPI:optimised}).
-
+The resulting sets are illustrated in Figure~\ref{figure:V:prime:and:comparison} and~\ref{fig:MRPI:optimised}.
 %
 \begin{figure}
-% \includegraphics[width=.95\linewidth]{Vprime.pdf}
-% \caption{The set~$\V^\prime$ resulting the optimisation~\eqref{seq:optimisation:MRPI:precise} for the discussed requirements in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow} with $\PP\{v\in\V^\prime\}=0.3$, and in \textcolor{red}{red}, the set satisfying~\eqref{eq:comparison:set}, with the defining samples.
+\includegraphics[width=.95\linewidth]{Vprime.pdf}
+\caption{The set~$\V^\prime$ resulting the optimisation~\eqref{seq:optimisation:MRPI:precise} for the discussed requirements in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow} with $\PP\{v\in\V^\prime\}=0.3$, and in \textcolor{red}{red}, the set satisfying~\eqref{eq:comparison:set}, with the defining samples.
 The comparison set contains $80.77$\% of the total volume of $\V$.}
-\includegraphics[width=0.99\linewidth]{Vprime.pdf}
-\caption{The set~$\V^\prime$ resulting from the optimisation \mbox{(\ref{seq:optimisation:MRPI:precise}a-d)} with $\PP\{v\in\V^\prime\}=0.3$ in \textcolor[rgb]{0.9255,0.6902,0.2078}{yellow}. 
-%
-In \textcolor{red}{red}, the set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b) for a confidence level of $1-\beta=0.999$. 
-%
-The samples $\{\hat{v}^{(1)},\ldots,\hat{v}^{(26)}\}$ are shown in \textcolor{blue}{blue}.}
 \label{figure:V:prime:and:comparison}
-% \vspace{2mm}
+\vspace{4mm}
 \end{figure}
 
-\begin{figure}[ht]
-\includegraphics[width=.99\linewidth]{MRPIsetOptimised.pdf}
-\caption{The guaranteed positively invariant set $X^\infty$ computed using~\mbox{(\ref{seq:optimisation:MRPI:precise}a-d)} in \textcolor[rgb]{0,0.5216,0.7373}{blue}, and in \textcolor[rgb]{1,0,0}{dashed red} the robust positively invariant set for the disturbance set $\V^\prime$ computed using~(\ref{eq:comparison:set}a-b) with a confidence level of $1-\beta = 0.999$.}
+\begin{figure}
+\includegraphics[width=.95\linewidth]{MRPIsetOptimised.pdf}
+% \caption{The guaranteed positively invariant set of the system~\eqref{eq:example:system:MRPI} in solid red, in dashed blue the robust positively invariant set for the disturbance set computed with the methods discussed in~\cite{Zhang2015}.}
+\caption{The guaranteed positively invariant set $X^\infty$ computed using~(\ref{seq:optimisation:MRPI:abstract}a-c) 
+%of the system~\eqref{eq:example:system:MRPI} 
+in \textcolor[rgb]{0,0.5216,0.7373}{blue}, and in \textcolor[rgb]{1,0,0}{dashed red} the robust positively invariant set for the disturbance set computed using the methods discussed in~\cite{Zhang2015} with
+%a confidence level of $0.999$.}
+confidence $1-\beta$, $\beta = 0.001$.}
 \label{fig:MRPI:optimised}
-\vspace{2mm}\end{figure}
+\vspace{4mm}\end{figure}
 
-% For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
-% %
-% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
+For the same setup~\eqref{eq:example:system:MRPI} we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=X^\infty$.
 %
-For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, with $\T=X^\infty$,
+Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
 %
-by solving (\ref{seq:optimisation:n:step:precise}a-d) for $C_1(X^\infty)$, $C_2(X^\infty)$, $C_3(X^\infty)$, where $X^\infty$ is the guaranteed positively invariant set computed via (\ref{seq:optimisation:MRPI:precise}a-d).
+For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
 %
-Again the results illustrated in Figure~\ref{fig:n:step:controllable:set} can be reproduced using different initial values even though the Hessian at the maximiser has a non-trivial nullspace. 
+by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
 %
-The figure also shows the controllable sets that are obtained, for the same target set (i.e.~$\T=X^\infty$), with a fixed set $\V^\prime$ which was computed using the sample based approach of~\citet{Zhang2015} by solving~(\ref{eq:comparison:set}a-b).
+Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
 %
-Clearly the high level of sub-optimality in this choice of $\V^\prime$, which is a consequence of the requirement for a high level of confidence of satisfaction of the chance constraint, translates to sub-optimality in the computed sets $C_n(X^\infty)$.
-\textcolor{red}{Did we not say that 5 sentences ago?}
-%
-% For the same system and constraints (\ref{eq:example:system:MRPI})-(\ref{eq:example:pconstriaint}) we approximate the guaranteed 3-step controllable set $\C_3(\T)$, where $\T=\{x:\norm{x}_\infty\leq 2\}$
-% %
-% by solving (\ref{seq:optimisation:n:step:set:abstract}a-c) for $C_1(\T)$, $C_2(\T)$, $C_3(\T)$.
-% %
-% Again the result illustrated in Figure~\ref{fig:n:step:controllable:set} is reproduced using different initial values although the Hessian at the maximiser has a non-trivial nullspace.
-% %
 
-% \begin{figure}
-% \includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
-% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (\textcolor[rgb]{0.4667,0.6745,0.1882}{in green}). 
-% % The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
-% % \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue). 
-% Sets $C_1(X^\infty)$, $C_2(X^\infty)$ and $C_3(X^\infty)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.
+\begin{figure}
+\includegraphics[width=.95\linewidth]{NStepSetOptimised.pdf}
+\caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (\textcolor[rgb]{0.4667,0.6745,0.1882}{in green}). 
+% The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
+% \caption{Approximation of the guaranteed 3-step controllable set for a box $\T$ (in blue). 
+Sets $C_1(X^\infty)$, $C_2(X^\infty)$ and $C_3(X^\infty)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.
 For comparison, the controllable sets obtained with~\eqref{eq:comparison:set} with
-% confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
-\begin{figure}[ht]
-\includegraphics[width=.99\linewidth]{NStepSetOptimised.pdf}
-% \caption{Approximation of the guaranteed 3-step controllable set for a guaranteed positive invariant set $X^\infty$ (in blue).
-The additional sets are remaining $C_1(X^\infty),C_2(X^\infty)$ and $C_3(X^\infty)$ dashed for the comparison set obtained with~\eqref{eq:comparison:set} and solid for the optimised~$\V^\prime$ obtained with the proposed method.}
-\caption{Approximation of the guaranteed 3-step controllable set for a $\T=X^\infty$ (in \textcolor[rgb]{0.4667,0.6745,0.1882}{green}).
-Sets $C_1(\T)$, $C_2(\T)$ and $C_3(\T)$ computed by optimising $\V^\prime$ using  (\ref{seq:optimisation:n:step:set:abstract}a-c) are shown in solid lines.
-For comparison, the controllable sets obtained for a fixed $\V^\prime$ computed using~(\ref{eq:comparison:set}a,b) with
-confidence $1-\beta= 0.999$ are shown in dashed lines.}
+confidence $1-\beta$, $\beta = 0.001$ are shown in dashed lines.}
 \label{fig:n:step:controllable:set}
@@
 %
-%The method we present is based on a simple restriction of the set $\V^\prime$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
+The method we present is based on a simple restriction of the set $\V^\prime\subseteq\V$ to be a parallelotope, which yields remarkable results in simulation and does not introduce non-convex constraints in the optimisation presented.
 %
@@
 %
-Future work will remove this restriction by approximating non-uniform probability densities as discrete distributions defined by collections of spatially distributed point masses.
+Future work will remove this restriction by approximating non-uniform probability distributions as discrete distributions defined by collections of spatially distributed point masses.
 %
 This would necessarily introduce a degree of uncertainty in the probability measure of $\V^\prime$.
-However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by a sample based approach), which would allow for a deterministic guarantee of constraint satisfaction.
+However the uncertainty would be subject to deterministic bounds (rather than the statistical bounds provided by sample based approaches), which would allow for guarantees of constraint satisfaction.
 

### 2017-02-28 draft.tex
Revert "version submitted 8 Nov"
This reverts commit 7e31bd6b6723bbb3d00d3853f7bee8125eb026ae.

--- 2016-11-08 draft.tex
@@
 \begin{keyword}                           % Five to ten keywords,  
-Robust control; chance constraints;  invariant sets; stochastic MPC.
+Robust control; chance constraints; stochastic MPC; positively invariant sets.
 \end{keyword}                             % keyword list or with the 

### 2017-03-03 draft.tex
updated statement and proof of Theorem 2 after review

--- 2016-11-08 draft.tex
@@
 
-\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}%\thanksref{footnoteinfo}} 
+\title{Maximising the guaranteed feasible set for stochastic MPC with chance constraints}
+%\title{Maximising the guaranteed feasible set for uncertain MPC schemes with chance constraints}%\thanksref{footnoteinfo}} 
 % Title, preferably not more than 10 words.
@@
 Robust control; chance constraints;  invariant sets; stochastic MPC. 
+%Robust control; chance constraints; stochastic MPC; positively invariant sets.
 \end{keyword}                             % keyword list or with the 
@@
 \begin{thm}\label{thm2}
-Let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in X_0$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that
+Assume that $K$ is chosen so that $\rho < 1$, where $\rho$ is the spectral radius of $A+BK$.
+Also let $\Gamma$ be a matrix such that $\Gamma x\leq\bfa{1}$ and $-\Gamma x\leq\bfa{1}$ for all $x\in X_0$ and let $\bigl((A+BK),\Gamma\bigr)$ be observable, then the iteration~\eqref{eq:MRPI:sequence} %terminates after a finite number, $N$, of iterations, such that
 yields $X_{k+1}=X_k$ for all $k\geq N$ and hence $X_k=X^\infty$ for some finite integer $N$.
@@
 %
-The matrix~$\Gamma$ is an analytical object and can be made up of~$E_i$ and~$F_iK$, but does not need to contain all inequalities supporting~$X_0$, e.g. in asymmetrical cases.
+The matrix~$\Gamma$ is introduced to simplify  analysis of the iteration~(\ref{eq:MRPI:sequence}).
+Note that the rows of $\Gamma$ can include~$E_i$ and~$F_iK$, but $\Gamma$ need not contain all hyperplanes supporting~$X_0$ (consider for example the case of asymmetrical constraints).
 %
@@
 \]
-holds, where $\rho$ denotes the spectral radius of $A+BK$, such a matrix can be found using semi-definite programming.
+holds (a suitable matrix $P$ can be found using semi-definite programming).
+%, where $\rho$ denotes the spectral radius of $A+BK$, 
+%such a matrix can be found using semi-definite programming.
 %
@@
 Clearly the high level of sub-optimality in this choice of $\V^\prime$, which is a consequence of the requirement for a high level of confidence of satisfaction of the chance constraint, translates to sub-optimality in the computed sets $C_n(X^\infty)$.
-\textcolor{red}{Did we not say that 5 sentences ago?}
+%\textcolor{red}{Did we not say that 5 sentences ago?}
 %
